---
title: "NutChl_2022HABs"
author: "Kristi Arend"
date: "11/11/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Origional code by Mine Berg mbearg@esassoc.com
#Updated by Rosemary Hartman (rosemary.hartman@water.ca.gov)
#Modified by Kristi Arend (karend@usbr.gov) for 2022 data, using code from plot_continuous_data.Rmd by Cat Pien

```{r}
library(plyr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(gridExtra)
library(sf)
library(ggmap)
library(dplyr)
library(readr)
library(here)
library(Polychrome)
library(viridis)
library(deltamapr)
library(ggspatial)
library(readxl)
library(patchwork)
library(cowplot)
library(here)

data_root = "analysis_2022/"
```

read in data file; this is for 2022 data only
load regions file

```{r}
hab_nutr_chla_mvi <- read_csv("data_clean/discrete_wq_2022.csv")
load(here::here("data","Regions.RData"))
```

Replace values below the reporting limits with zeros

```{r}
Nuts = mutate(hab_nutr_chla_mvi, Month = month(Date),
              Year = year(Date),Chlorophyll = as.numeric(Chlorophyll),
              Nitrate = as.numeric(DissNitrateNitrite),
              Phosphorus = as.numeric(DissOrthophos)) %>%
  dplyr::mutate(Chl = case_when(Chlorophyll_Sign == "<" ~ 0,
                         TRUE ~ Chlorophyll),
         Nitrate = case_when(DissNitrateNitrite_Sign == "<" ~ 0,
                             TRUE ~ Nitrate),
        Nitrate = case_when(DissNitrateNitrite_Sign == "< (estimated)" ~ 0,
                            TRUE ~ Nitrate),
         Phosphorus = case_when(DissOrthophos_Sign == "<" ~ 0,
                                TRUE ~ Phosphorus),
        Ammonium = as.numeric(DissAmmonia),
        Ammonium = case_when(DissAmmonia_Sign == "< (estimated)" ~ 0,
                            TRUE ~ Ammonium)) %>%
  dplyr::filter(Month %in% c(2, 3, 4, 5, 6,7,8,9,10,11))
```
UPDATE: should no longer be a problem; coordinates and data files updated on 3/2/23

A couple of the NCRO stations have different cdec codes than what NCRO uses and don't have lat and long coordinates; 
also, time stamps have 8 hours added to the original collection times because GMT used when creating 2022 data file

Insert correct WGS84 coordinates as follows:
Station MHR is really MHO: 37.87618, -121.383
Station OBD is really ODM: 37.81097, -121.544
Station RSL is really RSCC: 37.97619, -121.64

```{r}
#Nuts$Station[Nuts$Station == "MHR"] <- "MHO"
#Nuts$Station[Nuts$Station == "OBD"] <- "ODM"
#Nuts$Station[Nuts$Station == "RSL"] <- "RSCC"

#Nuts = dplyr::mutate(Nuts, Latitude = case_when(Station == "MHO" ~ 37.87618,
#                          TRUE ~ Latitude),
#  Longitude = case_when(Station == "MHO" ~ -121.383,
#                                           TRUE ~ Longitude),
#  Latitude = case_when(Station == "ODM" ~ 37.81097,
#                                           TRUE ~ Latitude),
#  Longitude = case_when(Station == "ODM" ~ -121.544,
#                                            TRUE ~ Longitude),
#  Latitude = case_when(Station == "RSCC" ~ 37.97619,
#                                           TRUE ~ Latitude),
#  Longitude = case_when(Station == "RSCC" ~ -121.640,
#                                           TRUE ~ Longitude))
```

Add 2014-2021 discrete water quality data from last year's report

Load data

Remove microcystis and region columns
```{r}
Nuts_pre22 <- read_csv(here::here("analysis_2022", "data_raw", "hab_nutr_chla_mvi.csv"))

Nuts_pre22_v2 <- subset(Nuts_pre22, select = -c(Region, Microcystis))
```

Manipulate data like did for 2022 and rearrange columns to match 2022

```{r}
Nuts_pre22_v3 = mutate(Nuts_pre22_v2, Month = month(Date),
              Year = year(Date),Chlorophyll = as.numeric(Chlorophyll),
              Nitrate = as.numeric(DissNitrateNitrite),
              Phosphorus = as.numeric(DissOrthophos)) %>%
  dplyr::mutate(Chl = case_when(Chlorophyll_Sign == "<" ~ 0,
                                TRUE ~ Chlorophyll),
                Nitrate = case_when(DissNitrateNitrite_Sign == "<" ~ 0,
                                    TRUE ~ Nitrate),
                Nitrate = case_when(DissNitrateNitrite_Sign == "< (estimated)" ~ 0,
                                    TRUE ~ Nitrate),
                Phosphorus = case_when(DissOrthophos_Sign == "<" ~ 0,
                                       TRUE ~ Phosphorus),
        Ammonium = as.numeric(DissAmmonia),
        Ammonium = case_when(DissAmmonia_Sign == "< (estimated)" ~ 0,
                            TRUE ~ Ammonium)) %>%
  dplyr::filter(Month %in% c(2, 3, 4, 5, 6,7,8,9,10,11)) %>%
  # rearrange columns to match 2022 dataframe
  dplyr::select(Source, Station, Latitude, Longitude,
                Date, Datetime, DissAmmonia, DissAmmonia_Sign, DissNitrateNitrite,
                DissNitrateNitrite_Sign, DissOrthophos, DissOrthophos_Sign,
                Chlorophyll, Chlorophyll_Sign, Month, Year, Nitrate, Phosphorus, Chl, Ammonium)

```

Combine 2022 data with 2014-2021 data

Select just the columns with the final nutrient/chlorophyll values (e.g., zeros in place of values below detection )

Convert to long form

```{r}
Nuts_all <- rbind(Nuts_pre22_v3, Nuts)

Nuts_Long = dplyr::select(Nuts_all, Source, Station, Latitude, Longitude, Date, Month, Year, Nitrate, Phosphorus, Chl, Ammonium) %>%
  gather(analyte,value, - c(Source, Station, Latitude, Longitude, Date, Month, Year))
```

Check start and end dates for the different data surveys/sources

```{r}
Nut_Summy <- Nuts_all %>%
  group_by(Source) %>%
  summarize(first=min(as.Date(Date)),last=max(as.Date(Date)))
```
Add the regional assignments

```{r}
nutssf = st_as_sf(Nuts_Long, coords = c("Longitude", "Latitude"), crs = 4326) %>%
  st_join(reg3) %>%
  st_drop_geometry() %>%
  # filter(!is.na(Region)) %>%
  mutate(Station = case_when(Source == "USGS_CAWSC" ~str_sub(Station, start = 6),
                             TRUE ~ Station))
```

PLOT ANNUAL MEANS

Calculate April - November means for each analyte and region across sampling programs and stations

```{r}
nuts_ann_mean = nutssf %>%
  dplyr::filter(!is.na(Stratum)) %>%
  dplyr::filter(Month %in% c(4,5,6,7,8,9,10,11)) %>%
  dplyr::group_by(Stratum2, Year, analyte) %>%
  dplyr::summarize(AnnMean = mean(value, na.rm = TRUE),
            SEc = sd(value, na.rm = T)/sqrt(n()),
            AnnMin = AnnMean - SEc,
            AnnMax = AnnMean + SEc)
  
```
Save the data to the data_clean folder
```{r}
write.csv(nuts_ann_mean,"C:/Users/karend/Desktop/HABs_AqVeg/EDB-HABs-Weeds/analysis_2022/data_clean/AllSources_DiscreteNuts_AnnualMeans_2014_2022.csv", row.names = FALSE)
```

Plot annual means for each analyte (row) by region (column)

First, specify the order you want Stratum2 to appear in the plots
Second, specify the order you want the analytes to appear

Plot North and East Delta together in one figure; plot South and Central Delta together in another figure

Export plots

```{r}
nuts_ann_mean$Stratum2 = factor(nuts_ann_mean$Stratum2, levels=c("Upper Sac","Cache/Liberty","Lower Sac","East Delta","Lower SJ","Franks","OMR","South Delta"))

nuts_ann_mean$analyte = factor(nuts_ann_mean$analyte, levels=c("Chl", "Ammonium", "Nitrate", "Phosphorus"))

nuts_ann_NEdelta = nuts_ann_mean %>%
  filter(Stratum2 %in% c("Upper Sac", "Cache/Liberty", "Lower Sac", "East Delta"))

nuts_ann_SCdelta = nuts_ann_mean %>%
  filter(Stratum2 %in% c("Lower SJ", "Franks", "OMR", "South Delta"))
  
plot_NEdelta_annNut = ggplot(nuts_ann_NEdelta, aes(x=Year, y = AnnMean, fill = Stratum2)) + geom_col()+
  geom_errorbar(aes(ymin = AnnMin, ymax = AnnMax))+
  facet_grid(analyte~Stratum2, scales = "free_y",
             labeller = as_labeller(c(`Upper Sac` = "Upper Sac", `Cache/Liberty` = "Cache/Liberty",
                                      `Lower Sac` = "Lower Sac",`East Delta` = "East Delta", Chl = "Chl a\n(ug/L)",
                                      Ammonium = "Ammon \n(mg/L)",Nitrate = "Nitrate \n(mg/L)",
                                      Phosphorus="Phos \n(mg/L)"))) +
  scale_fill_brewer(palette = "Set2", guide = NULL)+
  scale_x_continuous(n.breaks = 6)+ 
  ylab("Concentration")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2))

plot_SCdelta_annNut = ggplot(nuts_ann_SCdelta, aes(x=Year, y = AnnMean, fill = Stratum2)) + geom_col()+
  geom_errorbar(aes(ymin = AnnMin, ymax = AnnMax))+
  facet_grid(analyte~Stratum2, scales = "free_y",
             labeller = as_labeller(c(`Lower SJ` = "Lower SJ", `Franks` = "Franks",
                                      `OMR` = "OMR",`South Delta` = "South Delta", Chl = "Chl a\n(ug/L)",
                                      Ammonium = "Ammon \n(mg/L)",Nitrate = "Nitrate \n(mg/L)",
                                      Phosphorus="Phos \n(mg/L)"))) +
  scale_fill_brewer(palette = "Set2", guide = NULL)+
  scale_x_continuous(n.breaks = 6)+ 
  ylab("Concentration")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.2))

```

Put plots together using patchwork

```{r}
DiscNuts_annual_plots = plot_NEdelta_annNut / plot_SCdelta_annNut +  plot_annotation(tag_levels = 'A') #+  plot_layout(guides = 'collect')
```

Export plots

```{r}
#png(filename = here("analysis_2022/figures/Mean_AnnNuts_2014_2022.png"), width = 10, #height = 12, units = "in", pointsize = 12, family = "sans", res = 300)
#DiscNuts_annual_plots
#dev.off()

#ggsave(
#  here("analysis_2022/figures/Mean_AnnNuts_2014_2022.jpg"),
#  plot = DiscNuts_annual_plots, width = 15, height = 15, units = "in", pointsize = 12, #family = "sans")

jpeg("C://Users/karend/Desktop/HABs_AqVeg/EDB-HABs-Weeds/analysis_2022/figures/Mean_AnnNuts_2014_2022.jpg")
plot(DiscNuts_annual_plots,
     height = 12,
     width = 10,
     units = "in",
     pointsize = 12,
     family = "sans",
     res = 300)
dev.off()

```

Load TUCP dates

```{r}
tucp_dates <- read_excel(here::here("data/tucp_dates.xlsx"))%>%
  mutate(BarrierStartDate = lubridate::ymd(BarrierStartDate),
         BarrierEndDate = ymd(BarrierEndDate),
         TUCPStart = ymd(TUCPStart),
         TUCPEnd = ymd(TUCPEnd)) %>%
  dplyr::rename(WaterYear = `Water Year`)
```

Append TUCP dates to nutssf

```{r}
tucp_dates <- dplyr::rename(tucp_dates, Year = 'WaterYear')

nutssf_TUCP = nutssf %>%
 filter(Year > 2014) %>%
  left_join(tucp_dates) %>%
  mutate(TUCP_in_effect = case_when(TUCP == "Yes" & Date >= TUCPStart & Date <= TUCPEnd ~ "Yes",
                                    TRUE ~ "No"))
```

Add 2022 TUCP and barrier dates, because I can't get the code to work to pull from nnutssf_TUCP

```{r}
TUCP_22Dates <- as.Date(c(tucp_dates$TUCPStart[12],tucp_dates$TUCPEnd[12]))
Barrier_22Dates <- as.Date(c(tucp_dates$BarrierStartDate[12], tucp_dates$BarrierEndDate[12]))
```
Set analyte levels for plotting

```{r}
nutssf_TUCP$analyte = factor(nutssf_TUCP$analyte, levels=c("Chl", "Ammonium", "Nitrate", "Phosphorus"))
```

Subset data by stratum

```{r}
# CACHE
Cache_2022 = nutssf_TUCP %>%
  filter(Stratum2 %in% "Cache/Liberty",
         Year %in% 2022)

# LOWER SJ
LowSJ_2022 = nutssf_TUCP %>%
  filter(Stratum2 %in% "Lower SJ",
         Year %in% 2022)

# FRANKS
Franks_2022 = nutssf_TUCP %>%
  filter(Stratum2 %in% "Franks",
         Year %in% 2022)

# OMR
OMR_2022 = nutssf_TUCP %>%
  filter(Stratum2 %in% "OMR",
         Year %in% 2022)

# SOUTH DELTA
SDelta_2022 = nutssf_TUCP %>%
  filter(Stratum2 %in% "South Delta",
         Year %in% 2022)
```

WRITE CSV OF DATA USED FOR REPORT 

```{r fig.height=10, fig.width=12}
# write csv file
write.csv(nutssf_TUCP,"C:/Users/karend/Desktop/HABs_AqVeg/EDB-HABs-Weeds/analysis_2022/data_clean/DiscreteNuts_HABsReport_2014_2022.csv", row.names = FALSE)
```

LOAD REPORT DATA FILE

```{R}

nutssf_TUCP <- read_csv("data_clean/DiscreteNuts_HABsReport_2014_2022.csv")

```

PLOT 2022 DATA for each stratum

```{r}

# make a color palette
library(RColorBrewer)
pal = c(brewer.pal(8, "Set2"), brewer.pal(12, "Set3"), brewer.pal(9, "Set1"), brewer.pal(12, "Paired"), "black", "grey")

# create df with just station information
Disc_Nut_Stations = nutssf_TUCP %>%
  dplyr::select(Source, Station, Year, Stratum2, colors) %>%
  filter(Year %in% 2022,
         Stratum2 %in% c("Cache/Liberty","Lower SJ","Franks","OMR","South Delta")) %>%
  #group_by(Stratum2, Source, Station) %>%
  distinct(Stratum2, Source, Station)


# save csv of station IDs by monitoring program (source) and stratum
write.csv(Disc_Nut_Stations,"C:/Users/karend/Desktop/HABs_AqVeg/EDB-HABs-Weeds/analysis_2022/data_clean/DiscreteNut_Stations_2022.csv", row.names = FALSE)

#set width and height options
options(repr.plot.width =15, repr.plot.height =15)

#set up function to set equal y-axis breaks in the facets
equal_breaks <- function(n = 3, s = 0.5, ...){
  function(x){
    # rescaling
    d <- s * diff(range(x)) / (1+2*s)
    round(seq(min(x)+d, max(x)-d, length=n), 2)
  }
}
```  

```{r}
# CACHE
(plot_Cache_2022nuts = ggplot(Cache_2022,aes(x= Date, y = value, color = Station)) +
# add a shaded rectangle to show duration of TUCP
  geom_rect(aes(xmin = ymd(unique(TUCPStart)),
                xmax = ymd(unique(TUCPEnd)),
                   ymin = -Inf,
                   ymax = Inf),
               fill= "gray95", color = NA, alpha = 0.5)+
  geom_point() + geom_line() +
  facet_grid(analyte~., scales = "free_y", 
             labeller = as_labeller(c(Chl = "Chl a\n(ug/L)",Ammonium = "Ammon \n(mg/L)", 
                                      Nitrate = "Nitrate \n(mg/L)",Phosphorus="Phos \n(mg/L)"))) +
# add dotted lines to show start and end dates for emergency barrier
  geom_vline(aes(xintercept = BarrierStartDate), linetype = "dotted") +
   geom_vline(aes(xintercept = BarrierEndDate), linetype = "dotted") + 
  scale_x_date(breaks = "1 months", date_labels = "%b", expand = c(0,0)) + 
  scale_y_continuous(breaks=equal_breaks(n=3, s=0.5), 
                     expand = c(0.05, 0)) +
  labs(y = "Concentration", color = "Station") + 
  ggtitle("Cache/Liberty")+
  theme_bw() +
  theme(strip.text = element_text(size = 9),
         axis.text = element_text(size = 9),
         axis.title.x = element_blank(),
        legend.position = "none"))

        

# LOWER SJ
(plot_LowerSJ_2022nuts = ggplot(LowSJ_2022,aes(x= Date, y = value, color = Station)) +
# add a shaded rectangle to show duration of TUCP
  geom_rect(aes(xmin = ymd(unique(TUCPStart)),
                xmax = ymd(unique(TUCPEnd)),
                   ymin = -Inf,
                   ymax = Inf),
               fill= "gray95", color = NA, alpha = 0.5)+
  geom_point() + geom_line() +
  facet_grid(analyte~., scales = "free_y", 
             labeller = as_labeller(c(Chl = "Chl a\n(ug/L)",Ammonium = "Ammon \n(mg/L)", 
                                      Nitrate = "Nitrate \n(mg/L)",Phosphorus="Phos \n(mg/L)"))) +
# add dotted lines to show start and end dates for emergency barrier
  geom_vline(aes(xintercept = BarrierStartDate), linetype = "dotted") +
   geom_vline(aes(xintercept = BarrierEndDate), linetype = "dotted") + 
  scale_x_date(breaks = "1 months", date_labels = "%b", expand = c(0,0)) + 
  scale_y_continuous(breaks=equal_breaks(n=3, s=0.5), 
                     expand = c(0.05, 0)) +
  labs(y = "Concentration", color = "Station") + 
  ggtitle("Lower San Joaquin")+
  theme_bw() +
  theme(strip.text = element_text(size = 9),
         axis.text = element_text(size = 9),
         axis.title.x = element_blank(),
        legend.position = "none"))


# FRANKS
plot_Franks_2022nuts = ggplot(Franks_2022,aes(x= Date, y = value, color = Station)) +
# add a shaded rectangle to show duration of TUCP
  geom_rect(aes(xmin = ymd(unique(TUCPStart)),
                xmax = ymd(unique(TUCPEnd)),
                   ymin = -Inf,
                   ymax = Inf),
               fill= "gray95", color = NA, alpha = 0.5)+
  geom_point() + geom_line() +
  facet_grid(analyte~., scales = "free_y", 
             labeller = as_labeller(c(Chl = "Chl a\n(ug/L)",Ammonium = "Ammon \n(mg/L)", 
                                      Nitrate = "Nitrate \n(mg/L)",Phosphorus="Phos \n(mg/L)"))) +
# add dotted lines to show start and end dates for emergency barrier
  geom_vline(aes(xintercept = BarrierStartDate), linetype = "dotted") +
  geom_vline(aes(xintercept = BarrierEndDate), linetype = "dotted") + 
  scale_x_date(breaks = "1 months", date_labels = "%b", expand = c(0,0)) + 
  scale_y_continuous(breaks=equal_breaks(n=3, s=0.5), 
                     expand = c(0.05, 0)) +
  labs(y = "Concentration", color = "Station") + 
  ggtitle("Franks Tract")+
  theme_bw() +
  theme(strip.text = element_text(size = 9),
         axis.text = element_text(size = 9),
         axis.title.x = element_blank(),
        legend.position = "none")


# OMR
plot_OMR_2022nuts = ggplot(OMR_2022,aes(x= Date, y = value, color = Station)) +
# add a shaded rectangle to show duration of TUCP
  geom_rect(aes(xmin = ymd(unique(TUCPStart)),
                xmax = ymd(unique(TUCPEnd)),
                   ymin = -Inf,
                   ymax = Inf),
               fill= "gray95", color = NA, alpha = 0.5)+
  geom_point() + geom_line() +
  facet_grid(analyte~., scales = "free_y", 
             labeller = as_labeller(c(Chl = "Chl a\n(ug/L)",Ammonium = "Ammon \n(mg/L)", 
                                      Nitrate = "Nitrate \n(mg/L)",Phosphorus="Phos \n(mg/L)"))) +
# add dotted lines to show start and end dates for emergency barrier
  geom_vline(aes(xintercept = BarrierStartDate), linetype = "dotted") +
  geom_vline(aes(xintercept = BarrierEndDate), linetype = "dotted") + 
  scale_x_date(breaks = "1 months", date_labels = "%b", expand = c(0,0)) + 
  scale_y_continuous(breaks=equal_breaks(n=3, s=0.5), 
                     expand = c(0.05, 0)) +
  labs(y = "Concentration", color = "Station") + 
  ggtitle("OMR")+
  theme_bw() +
  theme(strip.text = element_text(size = 9),
         axis.text = element_text(size = 9),
         axis.title.x = element_blank(),
        legend.position = "none")
#+
#  labs(color = "OMR")

# SOUTH DELTA
plot_SDelta_2022nuts = ggplot(SDelta_2022,aes(x= Date, y = value, color = Station)) +
# add a shaded rectangle to show duration of TUCP
  geom_rect(aes(xmin = ymd(unique(TUCPStart)),
                xmax = ymd(unique(TUCPEnd)),
                   ymin = -Inf,
                   ymax = Inf),
               fill= "gray95", color = NA, alpha = 0.5)+
  geom_point() + geom_line() +
  facet_grid(analyte~., scales = "free_y", 
             labeller = as_labeller(c(Chl = "Chl a\n(ug/L)",Ammonium = "Ammon \n(mg/L)", 
                                      Nitrate = "Nitrate \n(mg/L)",Phosphorus="Phos \n(mg/L)"))) +
# add dotted lines to show start and end dates for emergency barrier
  geom_vline(aes(xintercept = BarrierStartDate), linetype = "dotted") +
  geom_vline(aes(xintercept = BarrierEndDate), linetype = "dotted") + 
  scale_x_date(breaks = "1 months", date_labels = "%b", expand = c(0,0)) + 
  scale_y_continuous(breaks=equal_breaks(n=3, s=0.5), 
                     expand = c(0.05, 0)) +
  labs(y = "Concentration", color = "Station") + 
  ggtitle("South Delta")+
  theme_bw() +
  theme(strip.text = element_text(size = 9),
         axis.text = element_text(size = 9),
         axis.title.x = element_blank(),
        legend.position = "none")
```

Put plots together using patchwork

```{r}
(Nuts_2022_plots = (plot_Cache_2022nuts + plot_LowerSJ_2022nuts + plot_Franks_2022nuts + plot_OMR_2022nuts + plot_SDelta_2022nuts ) + plot_layout(ncol = 2))
```

Export plots

```{r}
#ggsave(
#  here::here("analysis_2022/figures/2022_DiscNuts.jpg"),
#  plot = Nuts_2022_plots, width = 15, height = 15, units = "in", pointsize = 12, family = "sans")

png(filename = here::here("analysis_2022", "figures", "plot_nuts_2022.png"), width = 9, height = 8, units = "in", pointsize = 10, family = "sans", res = 300)
Nuts_2022_plots
dev.off()

# jpeg("C://Users/karend/Desktop/HABs_AqVeg/EDB-HABs-Weeds/analysis_2022/figures/2022_DiscNuts_030323.jpg")
# plot(Nuts_2022_plots,
#      height = 1000,
#      width = 1000,
#      units = "px",
#      pointsize = 12,
#      family = "sans")
# dev.off()



```
