---
title: "clean_toxins"
author: "Catarina Pien"
date: '2022-10-03'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages
```{r}
library(tidyverse)
library(lubridate)
library(sf)
library(readxl)
#library(DroughtData)
library(RColorBrewer)
library(deltamapr)
library(ggmap)
library(ggsn)

library(here)

root <- "analysis_2022/" # this is to tell here where to start
```

Color palette
```{r}
HABcol = data.frame(Color = brewer.pal(7, "Dark2"),
                    Genus = c( "Anabaenopsis", "Aphanizomenon","Cylindrospermopsis", "Dolichospermum" ,
                               "Microcystis","Oscillatoria","Planktothrix"))
```

**Data Sources: **

* DWR - SWP
* Water Board - fHAB Stockton Waterfront Labor Day
* EB Parks - Big Break
* Water Board/Nautilus - Stockton
* Prop 1 water samples
* USGS Water Samples
* USGS Spatt

# Read in files 
```{r}
ct_swp0 <- read_excel(here(root, "data_raw", "DFD_SWP_cyano_data_2-2-23.xlsx"))
site_swp <- read_excel(here(root, "data_raw", "DWR_SWP_Cyanotoxin_results_2022.xlsx"), sheet = "Sample Location Info") %>%
  janitor::clean_names(case = "big_camel") %>%
  rename(Site_Name = Name)
ct_wb0 <- read_csv(here(root, "data_raw", "SWB_fHAB_cyano_2022.csv")) %>%
  filter(!is.na(Result)) # data originally in pdf and imported into csv
ct_eb0 <- read_excel(here(root, "data_raw", "EBParks_BigBreak_Cyanotoxin_2022_upd.xlsx"), skip = 1) %>%
  filter(!is.na(Park))
# Note: Danger Advisory posted 7/14/22
ct_naut0 = read_excel(here(root, "data_raw", "Nautilus_HAB_Chlorophyll_Feb2023.xlsx"))
ct_usgs1 <- read_tsv(here(root, "data_raw", "USGS_cyanotoxins_WW.tsv"))
# Note: original usgs file is the tsv. I only used this file for its Tox_class column. 
ct_usgs0 <- read_csv(here(root, "data_raw", "USGS_cyanotoxins_all2022.csv"))
# Note: this is the updated file. 
site_usgs0 <- read_tsv(here(root, "data_raw", "USGS_cyanotoxins_SiteLatLon.tsv"))
ct_prop1 <- read_excel(here(root, "data_raw", "Prop1_cyanotoxin_watersamples_October2022_notext.xlsx"))
ct_restore <- read_excel(here(root, "data_raw", "RestoreDelta_StocktonHABS_2022_AllData.xlsx"))
ct_edb <- read_excel(here(root, "data_raw", "ToxinResults_Barriersampling_EH.xlsx"), sheet = "Toxindata")


plot(R_EDSM_Subregions_Mahardja)
```

## Spatt
ppb are discrete whole water samples, ng/g are SPATT data so may want to split up the below
```{r}
spatt_files_DSP <- list.files("analysis_2022/data_raw", pattern = "USGS_Spatt_DSP", full.names = TRUE)
spatt1 <- lapply(spatt_files_DSP, read_excel, sheet = "Total Toxin Summary") %>%
  bind_rows() %>%
  janitor::clean_names(case = "upper_camel") %>%
  rename(TotalAnabaenopeptinsPpb = TotalAnabaenopetinsPpb,
         TotalAnabaenopeptinsNgG = TotalAnabaenopetinsNgG) %>%
  mutate(across(TotalMicrocystinsPpb:TotalOtherToxinsNgG, ~ replace(., str_detect(., 'ND'), 0)),
         across(TotalMicrocystinsPpb:TotalOtherToxinsNgG, as.numeric))

spatt_files_MDM <- list.files("analysis_2022/data_raw", pattern = "USGS_Spatt_MDM", full.names = TRUE)
spatt2 <- lapply(spatt_files_MDM, read_excel, sheet = "Total Toxin Summary") %>%
  bind_rows() %>%
  janitor::clean_names(case = "upper_camel") %>%
  rename(TotalAnabaenopeptinsPpb = TotalAnabaenopetinsPpb,
         TotalAnabaenopeptinsNgG = TotalAnabaenopetinsNgG) %>%
  select(VialNumber, ProjectUniqueId, FieldId, StationNumber, SampleStartDate, SampleStartTimePst,
         TotalMicrocystinsPpb, TotalAnabaenopeptinsPpb, TotalAnatoxinsPpb, TotalCylindrospermopsinsPpb, TotalSaxitoxinsPpb, TotalOtherToxinsPpb, TotalMicrocystinsNgG, TotalAnabaenopeptinsNgG, TotalAnatoxinsNgG, TotalCylindrospermopsinsNgG, TotalSaxitoxinsNgG, TotalOtherToxinsNgG)%>%
  mutate(across(TotalMicrocystinsPpb:TotalOtherToxinsNgG, ~ replace(., str_detect(., 'ND'), 0)),
         across(TotalMicrocystinsPpb:TotalOtherToxinsNgG, as.numeric))

spatt = rbind(spatt1, spatt2)



spatt_files <- read_excel(here(root, "data_raw", "USGS_data_WW_Spatt_Microcystis_updated20230210.xlsx"), sheet = "tbl_data_SPATT_cyanotoxins")%>%
  pivot_longer(cols = `D-Asp3-Dhb7-RR (ng/g)`:`Desamidoylneosaxitoxin (ng/g)`,names_to = "Analyte", values_to = "Result") %>%
  mutate(Analyte = str_replace(Analyte,"ng/g", "" )) %>%
  mutate(Analyte = str_replace(Analyte," \\(\\)", "" )) %>%
  rename(Start_Datetime = `Start_timestamp_(PST)`,
         End_Datetime = `End_timestamp_(PST)`) %>%
  mutate(Start_Datetime = parse_date_time(Start_Datetime, "%y/%m/%d %H:%M:%S"),
         End_Datetime = parse_date_time(End_Datetime, "%y/%m/%d %H:%M:%S"),
         StartDate = date(Start_Datetime),
         EndDate = date(End_Datetime),
         NWIS_site_no = as.numeric(NWIS_site_no)) %>%
  mutate(Resultf = case_when(Result == "ND" ~ "0",
                             Result == "N/A" ~ NA,
                            TRUE ~ as.character(Result)),
         Result = as.numeric(Resultf),
         UniqueID = paste0(field_ID, "_", End_Datetime)) %>%
  left_join(ct_usgs1%>% select(Analyte, Tox_class) %>%unique()) %>%
  mutate(Tox_class = case_when(grepl("MC",Analyte) |grepl("Microcys", Analyte) | grepl("D-Asp3-", Analyte)|grepl("Leu1", Analyte)|grepl("Dha-LR", Analyte) ~ "Microcystins",
                               grepl("Nodularin", Analyte) ~ "Nodularins",
                              grepl("Anatoxin", Analyte)|grepl("ANTX", Analyte)|grepl("anatoxin", Analyte) ~ "Anatoxins",
                              grepl("Dolicho", Analyte) ~ "Dolichopspermum",
                              grepl("Anabaen", Analyte)|grepl("Oscillamide", Analyte) ~ "Anabaenopeptins",
                              grepl("STX", Analyte)| grepl("axitoxin", Analyte) ~ "Saxitoxin",
                              grepl("Cylindrospermopsin", Analyte)|grepl("CYN", Analyte)|grepl("Cylidrospermopsin", Analyte) ~ "Cylindrospermopsins",
                             TRUE ~ Analyte)) %>%
  rename(Site = field_ID) %>%
  filter(!(grepl("GTX", Analyte))) %>%
  filter(!(grepl("BMAA", Analyte))) %>%
left_join(site_usgs0 %>% select(NWIS_site_no, Site, dec_lat_va, dec_long_va)) %>%
  dplyr::select(SampleID = UniqueID, Station_Code = NWIS_site_no, Site_Name = Site, Latitude = dec_lat_va, Longitude = dec_long_va, Analyte = Tox_class, Result, StartDate, EndDate)%>%
  mutate(Year = year(StartDate)) %>%
  filter(Year == "2022")

spatt_summary <- spatt_files %>%
  group_by(Site_Name, Station_Code, Latitude, Longitude, Year, StartDate, EndDate, Analyte) %>% 
  summarize(Result = sum(Result, na.rm = TRUE))

write_csv(spatt_summary, here(root, "data_clean", "spatt_data.csv"))
```

# Format

## SWP
There is some method information in the DWR_SWP_cyano_data_2022.xlsx file that can be extracted if needed.

Had to estimate Latitude and Longitude for Lake Del Valle, Barker Slough PP, Banks PP
```{r}
#Get the species into a consistent format
unique(ct_swp0$`PTOX Species 1`)
ct_swp = ct_swp0 %>%
  select(Date, Station, Analyte, Result=`Result (ng/mL)`, Notes) 
  
  #mutate(Concentration = parse_number(`Result (ng/mL)`))
  #mutate(Species = case_when(
#   `PTOX Species 1` %in% c("Aphanizomenon cf. flos-aquae/klebahnii",
#                         "Aphanizomenon flos-aquae/klebahnii", "cf. Aphanizomenon") ~ "Aphanizomenon",
#   `PTOX Species 1` %in% c("Oscillatoria cf. perornata", "Oscillatorialean filament(s)") ~ "Oscillatoria",
#   `PTOX Species 1` %in% c("cf. Phormidium", "Phormidium/Microcoleus") ~ "Phormidium",
#   `PTOX Species 1` == "cf. Planktothrix" ~ "Planktothrix",
#   TRUE ~ `PTOX Species 1`
# ))

#Now pivot wider then longer so I can add in zeros
swp = ct_swp %>%
  filter(!is.na(Result)) %>%
  mutate(Result = case_when(Result == "ND" ~ "0",
                            TRUE ~ as.character(Result)),
         Result = as.numeric(Result)) %>%
  mutate(SampleID = paste0(Date, Station),
         Site_Name = case_when(Station == "NBA Barker Sl PP" ~ "Barker Slough Pumping Plant",
                                  Station == "Banks PP" ~ "Banks Pumping Plant",
                                  Station == "Clifton Court Forebay"~"Clifton Court Forebay Inlet",
                                  Station == "Dyer Res Outlet" ~ "Dyer Reservoir Outlet",
                                  grepl("Lake Del Valle", Station) ~ "Lake Del Valle",
                                  TRUE ~ Station),
         Method = NA,
         Comments = Notes) %>%
  left_join(site_swp %>% select(Site_Name, ApproximateGpsCoordinates, SampleLocation)) %>%
  separate(ApproximateGpsCoordinates, c("Latitude", "Longitude"), sep = ",") %>%
  mutate(Latitude = case_when(Station == "NBA Barker Sl PP" ~ 38.275900,
                              Station == "Banks PP" ~ 37.801944,
                              Site_Name == "Lake Del Valle" ~ 37.586130,
                              TRUE ~ as.numeric(Latitude)),
         Longitude = case_when(Station == "NBA Barker Sl PP" ~ -121.7965,
                              Station == "Banks PP" ~ -121.620278,
                              Site_Name == "Lake Del Valle" ~ -121.703795,
                              TRUE ~ as.numeric(Longitude)),
         Date = date(Date),
         Study = "SWP")%>%
  dplyr::select(SampleID, Station_Code = Station, Site_Name , Latitude, Longitude, Method, Analyte, Result, Comments, SampleDate = Date, Study)
  
  
  
#  pivot_wider(ct_swp, id_cols = c(Station, Date, Notes), names_from = Species,
#                       values_from = Concentration, values_fill = 0, values_fn = sum) %>%
#  dplyr::select(!`none observed`) %>%
#pivot_longer(cols = Dolichospermum:`Microcystis wesenbergii`, names_to = "Species") %>%
#  filter(!is.na(value)) %>%
glimpse(swp)

#quick plot
ggplot(swp, aes(x = as.factor(SampleDate), y = Result, fill = Analyte)) + geom_bar(stat = "identity")
```

## Water Board
```{r}

# Add lat/lon based on COC_20220824.pdf
wb <- ct_wb0 %>%
  mutate(Latitude = case_when(Station == "Buckley Cove" ~ 37.97717,
                              Station == "SJR @ Stockton GC" ~ 37.95416,
                              Station == "McLeod Lake" ~ 37.9536),
         Longitude = case_when(Station == "Buckley Cove" ~ -121.37543,
                              Station == "SJR @ Stockton GC" ~ -121.34397,
                              Station == "McLeod Lake" ~ -121.293),
         Station_Code = case_when(Station == "Buckley Cove" ~ "Buckley",
                              Station == "SJR @ Stockton GC" ~ "SJR_StocktonGC",
                              Station == "McLeod Lake" ~ "McLeadLake"),
         Result = ifelse(Result == "ND", 0, Result),
         Result = as.numeric(Result),
         Comments = "NA",
         Datetime = mdy_hm(Datetime),
         Date = date(Datetime),
         SampleID = paste0(Datetime, Station_Code),
         Study = "SWB") %>%
  dplyr::select(SampleID, Station_Code, Site_Name = Station, Latitude, Longitude, Method, Analyte=Target, Result, Comments, SampleDate = Date, Study)
```


## EB Parks

* Used lat/lon from old data
* Used some of the naming from old data
* Unfortunately lots of dates with no actual data. Left comments in in case we can use that in the text to indicate there was probably Microcystis.

```{r}
ebparks = ct_eb0 %>%
  mutate(Station_Code = "07BBkayaklaun",
         Latitude = 38.01245,
         Longitude = -121.7282,
         Date = as.Date(as.numeric(Date), origin = "1899-12-30"))%>%
  mutate(Result = case_when(`Toxin Result (ppb)` == "ND" ~ 0,
                            `Toxin Result (ppb)` == " > 50" ~ 50,
                            `Toxin Result (ppb)` == "0.01 ppb" ~ 0.01,
                            `Toxin Result (ppb)` == "> 10 ppb" ~ 10,
                            TRUE ~ as.numeric(`Toxin Result (ppb)`)),
         SampleID = paste0(Date, Site),
         Method = NA,
         Analyte = "Microcystins", Station = "BigBreak",
         Study = "East Bay Parks") %>%
  select(SampleID, Station_Code, Site_Name = Site, Latitude, Longitude, Method, Analyte, Result, Comments = Commments, SampleDate = Date, Study)
```

## Nautilus
```{r}
# There were some issues with missing and incorrect coordinates, so fixing that below:
naut_spatial <- ct_naut0 %>% filter(!is.na(Latitude)) %>%
  mutate(Longitude = ifelse(Longitude > 0, Longitude * -1, Longitude)) 

naut_latlon <- naut_spatial %>%
  dplyr::select(Location, Latitude, Longitude) %>%
  distinct() %>%
  group_by(Location) %>%
  summarize(Latitude = mean(Latitude),
            Longitude = mean(Longitude)) %>%
  ungroup()

naut_missinglatlon <- ct_naut0 %>% filter(is.na(Latitude)) %>%
  select(-Latitude, -Longitude) %>%
  left_join(naut_latlon) %>%
  dplyr::select(Location, `Sample Date`, `Sample Time`, Latitude, Longitude, everything())

naut_amended <- rbind(naut_spatial, naut_missinglatlon)

# Standardization code
naut = naut_amended %>%
  janitor::clean_names(case = "upper_camel") %>%
  mutate(SampleID = paste0(SampleDate, SampleTime, Location),
         Site_Name = NA, Comments = NA,
         Study = "Nautilus") %>%
  dplyr::select(SampleID, Station_Code = Location, Site_Name, Latitude, Longitude, Method, Analyte = Parameter, Result, Comments, SampleDate, Study) %>%
  mutate(Result = case_when(Result == "ND" ~ 0,
                            TRUE ~ as.numeric(Result))) %>%
  dplyr::filter(!is.na(Result))


```

## USGS
Lat/Lon is NAD83

need info on SJMS
```{r}
usgs <- ct_usgs0 %>%
 # janitor::clean_names(case = "snake") %>%
  pivot_longer(cols = `D-Asp3-Dhb7-RR (ppb)`:`GTX 2/3 TOTAL (ppb)`,names_to = "Analyte", values_to = "Result") %>%
  mutate(Analyte = str_replace(Analyte,"ppb", "" )) %>%
  mutate(Analyte = str_replace(Analyte,"ug/L", "" )) %>%
  mutate(Analyte = str_replace(Analyte," \\(\\)", "" )) %>%
  rename(Datetime = `Timestamp_(PST)`) %>%
  mutate(Datetime = parse_date_time(Datetime, "%y/%m/%d %H:%M:%S"),
         SampleDate = date(Datetime)) %>%
  mutate(Comments = NA,
         Resultf = case_when(Result == "ND" ~ "0",
                             Result == "N/A" ~ NA,
                            TRUE ~ as.character(Result)),
         Result = as.numeric(Resultf),
         Study = "USGS",
         Method = NA, 
         UniqueID = paste0(field_ID, "_", Datetime)) %>%
  left_join(ct_usgs1%>% select(Analyte, Tox_class) %>%unique()) %>%
  mutate(Tox_class = case_when(grepl("MC",Analyte) |grepl("Microcys", Analyte) | grepl("D-Asp3-", Analyte)|grepl("Leu1", Analyte)|grepl("Dha-LR", Analyte) ~ "Microcystins",
                               grepl("Nodularin", Analyte) ~ "Nodularins",
                              grepl("Anatoxin", Analyte)|grepl("ANTX", Analyte)|grepl("anatoxin", Analyte) ~ "Anatoxins",
                              grepl("Dolicho", Analyte) ~ "Dolichopspermum",
                              grepl("Anabaen", Analyte)|grepl("Oscillamide", Analyte) ~ "Anabaenopeptins",
                              grepl("STX", Analyte)| grepl("axitoxin", Analyte) ~ "Saxitoxin",
                              grepl("Cylindrospermopsin", Analyte)|grepl("CYN", Analyte)|grepl("Cylidrospermopsin", Analyte) ~ "Cylindrospermopsins",
                             TRUE ~ Analyte)) %>%
  rename(Site = field_ID) %>%
  filter(!(grepl("GTX", Analyte))) %>%
  filter(!(grepl("BMAA", Analyte))) %>%
left_join(site_usgs0 %>% select(NWIS_site_no, Site, dec_lat_va, dec_long_va)) %>%
  dplyr::select(SampleID = UniqueID, Station_Code = NWIS_site_no, Site_Name = Site, Latitude = dec_lat_va, Longitude = dec_long_va, Method, Analyte = Tox_class, Result, Comments, SampleDate, Study)

samples <- usgs %>%
  select(SampleDate, Site_Name) %>%
  unique() %>%
  mutate(month = month(SampleDate)) %>%
  group_by(Site_Name, month) %>%
  summarize(n = n())
    
```

## Prop 1

```{r}
prop1 <- ct_prop1 %>%
  janitor::clean_names(case = "upper_camel") %>%
  filter(!is.na(CollectionDate)) %>%
  mutate(Comments = NA,
         Resultf = case_when(McNodUgLTest1 == "ND" ~ "0",
                            TRUE ~ as.character(McNodUgLTest1)),
         Result = as.numeric(Resultf),
         Latitude = as.numeric(TargetLatitude),
         Longitude = as.numeric(TargetLongitude),
         Study = "Prop 1",
          SampleDate = date(CollectionDate),
         SampleID = paste0(CollectionDate, "_", Site)) %>%
  select(SampleID, Station_Code = Site, Site_Name = Site, Latitude , Longitude, Method, Analyte, Result, Comments, SampleDate , Study)
```

## EDB
```{r}
contsta <- read_excel("analysis_2022/data_clean/continuous_stations.xlsx") %>%
  rename(Station = StationCode)

edb <- ct_edb %>%
  janitor::clean_names(case = "upper_camel") %>%
  filter(!is.na(Date)) %>%
  mutate(Comments = NA,
         Resultf = case_when(Concentration == "ND" ~ "0",
                            TRUE ~ as.character(Concentration)),
         Result = as.numeric(Resultf),
         Study = "EDB", 
         Method = NA) %>%
  left_join(contsta, by = "Station") %>%  
  mutate(Latitude = ifelse(Station == "BET", 38.041092, Latitude),
         Longitude = ifelse(Station == "BET", -121.632187, Longitude)) %>%
  select(SampleID=SampleId, Station_Code = Station, Site_Name = Name, Latitude, Longitude, Method, Analyte, Result=Resultf, Comments, SampleDate = Date, Study)
```

## Restore the Delta
```{r}
restore <- ct_restore %>%
  janitor::clean_names(case = "upper_camel") %>%
  filter(!is.na(CollectionDate),
         !is.na(SampleId)) %>%
  pivot_longer(cols = MicrocystinRrPpb:CylindrospermopsinPpb, names_to = "Analyte", values_to = "Result") %>%
  mutate(Comments = NA,
         Resultf = case_when(Result == "bdl" ~ "0",
                            TRUE ~ as.character(Result)),
         Result = as.numeric(Resultf),
         Study = "Restore the Delta", 
         Method = NA) %>%
  select(SampleID= SampleId, Station_Code = StationId, Site_Name = StationName, Latitude, Longitude, Method, Analyte, Result, Comments, SampleDate = CollectionDate, Study)
```



# Combine data

* SWP, Spatt, Stockton, Prop1, Nautilus, EastBay

```{r}
ct_all0 <- rbind(swp, wb, ebparks, naut, usgs, prop1, restore, edb) %>%
  mutate(Analyte2 = case_when(grepl("MC",Analyte) |grepl("Microcys", Analyte) | grepl("D-Asp3-", Analyte)|grepl("Leu1", Analyte)|grepl("Dha-LR", Analyte)|grepl("Nodularin", Analyte) ~ "Microcystins/Nodularins",
                              grepl("Anatoxin", Analyte)|grepl("ANTX", Analyte)|grepl("anatoxin", Analyte) ~ "Anatoxins",
                              grepl("Dolicho", Analyte) ~ "Dolichopspermum",
                              grepl("Anabaen", Analyte)|grepl("Oscillamide", Analyte) ~ "Anabaenopeptins",
                              grepl("STX", Analyte) ~ "Saxitoxin",
                              grepl("Cylindrospermopsin", Analyte)|grepl("CYN", Analyte)|grepl("Cylidrospermopsin", Analyte) ~ "Cylindrospermopsins",
                             TRUE ~ Analyte),
         Longitude = ifelse(Longitude>0, Longitude * -1, Longitude)) %>%
         filter(!is.na(Result)) %>%
  mutate(Result = as.numeric(Result))

ct_all <- ct_all0 %>%
  select(-Analyte, -Comments) %>%
  group_by(SampleID, Station_Code, Site_Name, Latitude, Longitude, Method, SampleDate, Study, Analyte2) %>%
  summarize(Result = sum(Result)) %>%
  rename(Analyte = Analyte2)

# Turn to sf 
ct_all_sf <- ct_all %>%
  filter(!is.na(Latitude)) %>%
  st_as_sf(coords =c("Longitude", "Latitude"), remove = FALSE)
st_crs(ct_all_sf) <- 4269
ct_all_sf <- st_transform(ct_all_sf, crs = 4326)

# 2022 
ct_2022_sf <- st_join(ct_all_sf, reg3)%>%
  mutate(Year = lubridate::year(SampleDate),
         Month = lubridate::month(SampleDate)) %>%
  dplyr::select(Station = Station_Code, 
                StationName = Site_Name,
         Date = SampleDate,
         Year, Month,
         Analyte,
         Method,
         Result,
         Study,
         Stratum2, 
         geometry)%>%
  filter(Year>2021) %>%
  #mutate(Advisory = replace(Advisory, Advisory == "NA", NA)) %>%
  mutate(Stratum2 = ifelse(Station %in% c("Dyer Res Outlet", "Clifton Court Forebay", "Banks PP"), "CCF", Stratum2))


filter(ct_all_sf, year(SampleDate) == "2022")
```

## Bring in 2021
```{r}
load("./data/Regions.RData")
ct_2021 <- read_csv(here(root, "data_clean", "ct_all_2021.csv")) %>%
  rename(Result = result) %>%
  mutate(StationName = NA,
         Date = ymd(Date),
         Year = year(Date),
         Month = month(Date),
         Method = NA,
         Study = case_when(Study == "Nautalis" ~ "Nautilus",
                           Study == "Preece" ~ "Prop 1",
                           Study == "EastBay" ~ "East Bay Parks",
                           Study == "DWR" ~ "SWP",
                           Study == "CVRWQCB" ~ "SWB",
                           TRUE ~ Study)) %>%
  select(Station, StationName, Date, Year, Month, Analyte, Method, everything())%>%
select(-Region)

ct_2021_sf <- ct_2021 %>%
  mutate(ll = gsub("c", "", geometry)) %>%
  mutate(ll = gsub("\\(", "", ll),
         ll = gsub("\\)", "", ll)) %>%
  separate(ll, into = c("Longitude", "Latitude"), sep = ",")%>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326) 

```

## Join
```{r}
ct_2021_2022 <- rbind(ct_2021_sf, ct_2022_sf)%>% select( -StationName, -Method) %>%
  mutate(Analyte = case_when(grepl("MC",Analyte) |grepl("Microcys", Analyte) | grepl("D-Asp3-", Analyte)|grepl("Leu1", Analyte)|grepl("Dha-LR", Analyte)|grepl("Nodularin", Analyte) ~ "Microcystins/Nodularins",
                              TRUE ~ Analyte))
```




# Add warnings
```{r}
ct_all_years = ct_2021_2022 %>%
  #filter(Analyte2 %in% c("Microcystins", "Anatoxins")) %>%
  mutate(Advisory = case_when(Analyte == "Microcystins/Nodularins" & Result > 0.8 & Result < 6 ~ "Caution",
                                                 Analyte == "Microcystins/Nodularins"  & Result >= 6 & Result < 20 ~ "Warning",
                                                 Analyte == "Microcystins/Nodularins"  & Result >= 20 ~ "Danger",
                                                 Analyte == "Microcystins/Nodularins"  & Result < 0.8 ~ "No Advisory",
                                               Analyte == "Anatoxins" & Result > 20 & Result <90 ~ "Warning",
                                               Analyte == "Anatoxins"  & Result > 0 & Result < 20 ~ "Caution",
                                               Analyte == "Anatoxins"  & Result == 0 ~ "No Advisory",
                              Analyte == "Cylindrospermopsin" & Result >=4 & Result < 17 ~ "Warning",
                              Analyte == "Cylindrospermopsin" & Result >=1 & Result <4 ~ "Caution",
                              Analyte == "Cylindrospermopsin" & Result < 1 ~ "No Advisory",
                              TRUE~NA))
```


```{r}
mapview::mapview(ct_all_years)
ggplot() + geom_sf(data = R_EDSM_Subregions_Mahardja) +
  geom_sf(data = ct_2022)
```

```{r}
ct_2022_forICF <- st_join(ct_all_sf, reg3)%>%
  mutate(Year = lubridate::year(SampleDate),
         Month = lubridate::month(SampleDate)) %>%
  dplyr::select(Station = Station_Code, 
                StationName = Site_Name,
         Date = SampleDate,
         Year, Month,
         Analyte = Analyte2,
         Method,
         Result,
         Advisory,
         Study,
         Stratum2,
         Latitude,
         Longitude,
         geometry)%>%
  mutate(Advisory = replace(Advisory, Advisory == "NA", NA)) %>%
  mutate(Stratum2 = ifelse(Station %in% c("Dyer Res Outlet", "Clifton Court Forebay", "Banks PP"), "CCF", Stratum2)) %>%
  filter(Analyte!= "Pheophytin a",
         Analyte!= "Chlorophyll a")

write_csv(ct_2022_forICF, "analysis_2022/data_clean/cyano_data_for_ICF.csv")
st_write(ct_2022_forICF, "analysis_2022/data_clean/cyano_data_for_ICF.shp")
```


# Write data
```{r}
ct_2022_only_sf <- ct_all_years %>% filter(Year == 2022)
saveRDS(ct_2022_only_sf, here(root, "data_clean", "ct_all_2022.rds"))
saveRDS(ct_all_years, here(root, "data_clean", "ct_all_years.rds"))
```

