---
title: "get_continuous_wq"
author: "Catarina Pien"
date: '2022-09-29'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(data.table) #rbindlist()
library(lubridate) #today()
library(CDECRetrieve) #cdec_datasets
library(readr)
library(here)
library(readxl)

data_root = "analysis_2022/data_raw/"
```

# Download CDEC

Based on df_WQ_daily.RData:
  * Stations: **CDEC: FAL, FRK, HLT, HOL, MDM, ORQ, OSJ**
  * Parameters: **Chl.a, DO, SpCond, Temp, Turb, pH, Flow**

NCRO: FAL, HLT, HOL, OSJ
EMP: FRK
USGS: MDM USGS 11312676, ORQ = USGS 11313434 


## Define cdec stations, time period
```{r}
### Define list of stations ----------------------------------
stations <- c("FAL", "FRK", "HLT", "HOL", "OSJ")

# Define start and end dates - these will remain the same throughout
start <- "2015-01-01"
end <- "2022-10-01"
```

## get flow data
```{r}
interval <- "E" # Event = every 15 minutes, H = Hourly, A = Annual
### Download data, bind, write --------------------------------------------
flow <- lapply(stations, 
                 function(x){
                   cdec_query(station = x,
                              sensor_num = 20,
                              dur_code = interval,
                              start_date = start,
                              end_date = end)
                   
                 })
flow_df <- bind_rows(flow) # bind rows into data frame
flow_clean <- flow_df %>%
    mutate(parameter = "flow", 
           datetime = ymd_hms(datetime),
           date = date(datetime)) %>%
  select(datetime,date,station = location_id,parameter,value = parameter_value) %>%
  filter(!is.na(value),
         !is.na(station)) 


flow_sum <- flow_clean %>%
  group_by(station) %>%
  summarize(n = n())
```

```{r}
saveRDS(flow_clean, here(data_root,"CDEC_flow_FAL_HLT_HOL_OSJ_2015_2022.rds"))
flow_clean <- readRDS(here(data_root,"CDEC_flow_FAL_HLT_HOL_OSJ_2015_2022.rds"))
```

## get velocity data
```{r}
interval <- "E" # Event = every 15 minutes, H = Hourly, A = Annual
### Download data, bind, write --------------------------------------------
vel <- lapply(stations, 
                 function(x){
                   cdec_query(station = x,
                              sensor_num = 21,
                              dur_code = interval,
                              start_date = start,
                              end_date = end)
                 })
velocity_df <- bind_rows(vel) # bind rows into data frame
vel_clean <- velocity_df %>%
  select(station = location_id,
         datetime,
         velocity = parameter_value) %>%
  filter(!is.na(velocity),
         !is.na(station))
velocity_sum <- vel_clean %>%
  group_by(station) %>%
  summarize(n = n())
```

# Read in other data
* NCRO
* EMP


## NCRO 

450 – Water Temperature in degrees Celsius
630 – Depth in Meters
810 – Turbidity in Formazin Nephelometric Units
821 – Specific Conductance in microSiemens per centimeter
865 – Dissolved Oxygen in percent Saturation
2351 – Dissolved Oxygen concentration in milligrams per Liter
7004 – Chlorophyll in micrograms per Liter

Data Quality Description
1	Good data
40	Fair measurement
120	Poor Measurement
151	Data Missing
170	Unreliable Data

### Functions to clean everything up (one for those with chlorophyll data, one without)

* Kept data that was scored 1 or 40, removed the rest
```{r}
# For 7 parameter data (including chlorophyll)
f_cleanparam <- function(sta, param, enddate) {
  # rename variables in a pattern to prepare for pivot
  df <- read.csv(here(data_root, paste0("NCRO_Continuous_WQ_", sta, "_20220101-",enddate, ".CSV")), skip = 1) %>%
  rename(datetime = and,
         p_wtemp = X450,
         p_depth = X630,
         p_turbidity = X810,
         p_spc = X821,
         p_dopct = X865,
         p_do = X2351,
         p_chl = X7004,
         q_wtemp = X,
         q_depth = X.1,
         q_turbidity = X.2,
         q_spc = X.3, 
         q_dopct = X.4,
         q_do = X.5, 
         q_chl = X.6) %>%
  mutate(across(p_wtemp:q_chl, as.numeric)) %>%
  subset(datetime != "Date") %>%
  mutate(datetime = mdy_hm(datetime),
         date = date(datetime),
         station = sta) %>%
  select(datetime, date, station, everything())
  
  # pivot_longer to be able to group by parameter
  df_long <- df %>%
  pivot_longer(cols = c(p_wtemp:q_chl), 
               names_to = c("type", "parameter"),
               names_sep = "_",
               values_to = "value")
  
  # subset to parameter
  param_df <- df_long %>%
  filter(parameter == param) %>%
  pivot_wider(names_from = "type", values_from = "value") %>%
  filter(q<120) %>%
  rename(value = p)%>%
    select(-q)
  
  return(param_df)
}

# For data without chlorophyll
f_cleanparam2 <- function(sta, param, enddate) {
  # rename variables in a pattern to prepare for pivot
  df <- read.csv(here(data_root, paste0("NCRO_Continuous_WQ_", sta, "_20220101-",enddate, ".CSV")), skip = 1) %>%
  rename(datetime = and,
         p_wtemp = X450,
         p_depth = X630,
         p_turbidity = X810,
         p_spc = X821,
         p_dopct = X865,
         p_do = X2351,
         q_wtemp = X,
         q_depth = X.1,
         q_turbidity = X.2,
         q_spc = X.3, 
         q_dopct = X.4,
         q_do = X.5) %>%
  mutate(across(p_wtemp:q_do, as.numeric)) %>%
  subset(datetime != "Date") %>%
  mutate(datetime = mdy_hm(datetime),
         date = date(datetime),
         station = sta) %>%
  select(datetime, date, station, everything())
  
  # pivot_longer to be able to group by parameter
  df_long <- df %>%
  pivot_longer(cols = c(p_wtemp:q_do), 
               names_to = c("type", "parameter"),
               names_sep = "_",
               values_to = "value")
  
  # subset to parameter
  param_df <- df_long %>%
  filter(parameter == param) %>%
  pivot_wider(names_from = "type", values_from = "value") %>%
  filter(q<120) %>%
  rename(value = p)%>%
    select(-q)
  
  return(param_df)
}

# Missing do
f_cleanparam3 <- function(sta, param, enddate) {
  # rename variables in a pattern to prepare for pivot
  df <- read.csv(here(data_root, paste0("NCRO_Continuous_WQ_", sta, "_20220101-",enddate, ".CSV")), skip = 1) %>%
  rename(datetime = and,
         p_wtemp = X450,
         p_depth = X630,
         p_turbidity = X810,
         p_spc = X821,
         p_chl = X7004,
         q_wtemp = X,
         q_depth = X.1,
         q_turbidity = X.2,
         q_spc = X.3, 
         q_chl = X.4) %>%
  mutate(across(p_wtemp:q_chl, as.numeric)) %>%
  subset(datetime != "Date") %>%
  mutate(datetime = mdy_hm(datetime),
         date = date(datetime),
         station = sta) %>%
  select(datetime, date, station, everything())
  
  # pivot_longer to be able to group by parameter
  df_long <- df %>%
  pivot_longer(cols = c(p_wtemp:q_chl), 
               names_to = c("type", "parameter"),
               names_sep = "_",
               values_to = "value")
  
  # subset to parameter
  param_df <- df_long %>%
  filter(parameter == param) %>%
  pivot_wider(names_from = "type", values_from = "value") %>%
  filter(q<120) %>%
  rename(value = p)%>%
    select(-q)
  
  return(param_df)
}
```

### Run functions to clean the data and combine data
```{r}
plist <- c("wtemp","depth","turbidity","spc","dopct","do","chl")  
data_FAL <- map(plist, ~ f_cleanparam(sta = "FAL", param = .x, enddate = "20220926")) %>% bind_rows()
data_OSJ <- map(plist, ~ f_cleanparam(sta = "OSJ", param = .x, enddate = "20220926")) %>% bind_rows()
data_HLT <- map(plist[-(5:6)], ~ f_cleanparam3(sta = "HLT", param = .x, enddate = "20220908")) %>% bind_rows()
data_HOL <- map(plist[1:6], ~ f_cleanparam2(sta = "HOL", param = .x, enddate = "20220823")) %>% bind_rows()
data_NCRO <- rbind(data_FAL, data_HOL, data_HLT, data_OSJ)
```

# EMP
```{r}
FRK0 <- read_csv(here(data_root, "EMP_Continuous_FRK_2022.csv"))

FRK <- FRK0 %>%
  mutate(date = date(datetime)) %>%
  rename(wtemp = watertemp_C,
         do = `dissolvedoxygen_mg/l`,
         chl = `fluorescence_ug/l`,
         pH = ph, 
         turbidity = turbidity_FNU,
         spc = `specificconductivity_uS/cm`) %>%
  pivot_longer(cols = do:wtemp, names_to = "parameter", values_to = "value") %>%
  select(datetime, date, station, parameter, value)
```


## USGS

00010 = water temperature, C
00011 = water temperature, F
00300 = dissolved oxygen
00301 = do_pct
00480 = salinity
00060 = discharge, cfs
00065 = gage height
63680 = turbidity, NTU
00095 = SPC, uS/cm @ 25 C
00400 = pH, water, unfiltered, field
32316 = fCHL, water, in situ 
72137 = tidally filtered discharge
72255 = mean water velocity
https://help.waterdata.usgs.gov/codes-and-parameters/parameters
https://help.waterdata.usgs.gov/code/parameter_cd_query?fmt=rdb&group_cd=PHY&inline=true

```{r}
f_get_NWIS <- function(siteNumbers=11312676, parameterCd = c('00010','63680', '00095', '00400', '00300', '32316'), startDate = "2022-01-01", endDate = "2022-10-01", tz = "Etc/GMT+8"){

  # get data
  print("Downloading data...")
  data <- dataRetrieval::readNWISuv(siteNumbers, parameterCd, startDate, endDate, tz)

  # fix names

  data2 <- dataRetrieval::renameNWISColumns(data)

  print("Data downloaded!")

  # clean names
  data2 <- janitor::clean_names(data2)

  # write out
  saveRDS(data2, paste0("analysis_2022/data_raw/USGS_NWIS_", siteNumbers, "_WQ.rds"))

  # print message!
  print("Data saved in data_raw")
}

f_get_NWIS_flow <- function(siteNumbers=11312676, parameterCd = c('00060'), startDate = "2015-01-01", endDate = "2022-10-01", tz = "Etc/GMT+8"){

  # get data
  print("Downloading data...")
  data <- dataRetrieval::readNWISuv(siteNumbers, parameterCd, startDate, endDate, tz)

  # fix names

  data2 <- dataRetrieval::renameNWISColumns(data)

  print("Data downloaded!")

  # clean names
  data2 <- janitor::clean_names(data2)

  # write out
  saveRDS(data2, paste0("analysis_2022/data_raw/USGS_NWIS_", siteNumbers, "_flow.rds"))

  # print message!
  print("Data saved in data_raw")
}
```

MDM: Latitude 37°56'34",   Longitude 121°31'59"   NAD27
ORQ: Latitude 38°01'38",   Longitude 121°33'52"   NAD83
DSJ: Latitude 38°00'49",   Longitude 121°40'00"   NAD27 38.01361 -121.6667
DUTCH SLOUGH BL JERSEY ISLAND RD A JERSEY ISLAND: 
```{r}
f_get_NWIS(siteNumbers = 11312676)
f_get_NWIS_flow(siteNumbers=11312676)
f_get_NWIS_flow(siteNumbers=11313434)
f_get_NWIS(siteNumbers = 11313433, startDate = "2015-01-01")
f_get_NWIS_flow(siteNumbers = 11313433)
```

```{r}
MDM <- read_csv(here(data_root, "USGS_NWIS_11312676_WQ.csv"))
MDMf <- readRDS(here(data_root, "USGS_NWIS_11312676_flow.rds")) %>%
  mutate(site_no = as.numeric(site_no)) 
MDM_comb <- left_join(MDMf, MDM) %>%
  rename(Datetime = date_time, 
         wtemp = wtemp_inst,
         flow = flow_inst,
         spc = spec_cond_inst,
         do = do_inst,
         pH = p_h_inst,
         turbidity = ts213_ysi_exo_turb_inst,
         chl = x_32316_inst)%>%
  mutate(station = "MDM",
         date = date(Datetime),
         datetime = Datetime) %>%
  select(datetime, date, station, wtemp, flow, spc, do, pH, turbidity,chl) %>%
  pivot_longer(cols = wtemp:chl,
               names_to = "parameter",
               values_to = "value") %>%
  filter(!is.na(value))

ORQ <- readRDS(here(data_root, "USGS_NWIS_11313434_flow.rds")) %>%
  rename(Datetime = date_time, 
         flow = flow_inst)%>%
  mutate(station = "ORQ",
         date = date(Datetime),
         datetime = Datetime) %>%
  select(datetime, date, station, flow) %>%
  pivot_longer(cols = flow,
               names_to = "parameter",
               values_to = "value")

DSJ_WQ <- readRDS(here(data_root, "USGS_NWIS_11313433_WQ.rds"))
DSJ_flow <- readRDS(here(data_root, "USGS_NWIS_11313433_flow.rds"))
DSJ <- left_join(DSJ_WQ, DSJ_flow) %>%
  rename(Datetime = date_time, 
         flow = flow_inst,
         wtemp = wtemp_inst,
         spc = spec_cond_inst,
         turbidity = ts213_ysi_exo_turb_inst)%>%
  mutate(station = "DSJ",
         date = date(Datetime),
         datetime = Datetime) %>%
  select(datetime, date, station, wtemp, spc, turbidity, flow) %>%
  pivot_longer(cols = wtemp:flow,
               names_to = "parameter",
               values_to = "value")

data_USGS <- rbind(MDM_comb, ORQ, DSJ) 
```

### Combine data from different programs
```{r}
wq_2022 <- rbind(data_NCRO, FRK, data_USGS, flow_clean) 
```

### Convert to daily info
```{r}
wq_2022_daily <- wq_2022 %>%
  group_by(station, date, parameter) %>%
  summarize(Daily.Mean = round(mean(value, na.rm = TRUE),2),
            Daily.Max = max(value, na.rm = TRUE),
            Daily.Min = min(value, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Year = year(date),
         Julian = yday(date),
         Month = month(date, label = TRUE)) %>%
rename(Site = station,
       Analyte = parameter, 
       Date = date) %>%
  filter(Analyte != "depth",
         Analyte != "dopct") %>%
  mutate(Analyte = case_when(Analyte == "chl" ~ "Chl.a",
                             Analyte == "do" ~ "DO.Conc",
                             Analyte == "spc" ~ "SpCond",
                             Analyte == "wtemp" ~ "Temp",
                             Analyte == "turbidity" ~ "Turb",
                             Analyte == "flow" ~ "Flow",
                             TRUE ~ Analyte)) %>%
  select(Site, Date, Analyte, Daily.Mean, Daily.Max, Daily.Min, Year, Julian, Month) %>%
  filter(!is.infinite(Daily.Min),
         !is.na(Date))

unique(wq_2022_daily$Analyte)
```


### Combine with previous year data
```{r}
load(here("data", "WQ.daily.RData"))
wq_all <- rbind(wq_2022_daily, WQ.daily)

summary(wq_all)
```

### Combine with coordinates 
```{r}
stalatlon <- read_excel(here(data_root, "../data_clean", "continuous_stations.xlsx")) %>%
  dplyr::select(-Type) %>%
  rename(Site = StationCode)

unique(wq_all$Site)

wq_all <- left_join(wq_all, stalatlon)
wq_2022 <- left_join(wq_2022_daily, stalatlon)
```

### Write file
```{r}
saveRDS(wq_all, here(data_root, "../data_clean", "continuous_wq_2015_2022.rds"))
saveRDS(wq_2022, here(data_root, "../data_clean", "continuous_wq_2022_allvals.rds"), compress = "xz")
```

