---
title: "model_microcystis"
author: "Catarina Pien"
date: '2022-12-07'
output: html_document
editor_options: 
  chunk_output_type: console
---

Look at effect of year and season on absence/presence data for Microcystis
Data updated through November 2022.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(sf)
library(lubridate)
library(here)

# didn't really need these
library(DHARMa)
library(visreg)
library(MASS)
library(car)
```

```{r}
#load(here("analysis_2022", "data_clean", "HABsw2022.RData"))
load(here("data","Regions.RData"))
microcystis <- read_csv(here("analysis_2022", "data_clean","HABsVis_final_2007_2022.csv"))

# Probably didn't need all of this given we are not looking at region. But just in case, it is in this dataset.
mic_region <- microcystis %>%
  filter(!is.na(Latitude)) %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326, remove = FALSE) %>%
  st_join(reg3) %>%
  #st_join(R_EDSM_Strata_1718P1, join = st_intersects) %>%
  st_drop_geometry() %>%
  # Remove any stations outside of the R_EDSM_Strata_1718P1 strata and from
    # Western Delta since there are so few observations with Microcystis present
    # in this region
  filter(
    !is.na(Stratum)) %>%
  mutate(
    # Convert Stratum to factor and rename it Region
#    Region = factor(Stratum, levels = vec_strata_levels, labels = vec_strata_labels),
    Region = factor(Stratum2),
    fYear = factor(Year),
    # Convert Microcystis to factor
#    Microcystis = factor(Microcystis, labels = c("Absent", "Low", "Medium", "High", "Very High"))

  ) %>%
  # Clean up data frame
  dplyr::select(
    Source,Station,Region,
    Latitude,
    Longitude,
    Date,
    Month,
    fYear,
    Year,
    Microcystis,
    MicroPA
  ) 
```

Filter to just seasons where there is Microcystis.
Filter to 2017+, when NCRO starts recording score. 
Remove USGS, since they only started 2022.
```{r}
mic_data <- mic_region %>%
  mutate(Station = factor(Station),
         Region = factor(Region),
         fYear = factor(Year),
         Season = case_when(Month %in% c(9,10,11)~ "Fall",
                            Month %in% c(12,1,2)~ "Winter",
                            Month %in% c(3,4,5)~ "Spring",
                            Month %in% c(6,7,8)~ "Summer"),
         Season = factor(Season, levels = c("Spring", "Summer", "Fall")),
         MicroPA = factor(MicroPA),
         fMonth = factor(Month)) %>%
  filter(#Season %in% c("Spring", "Summer", "Fall"),
        fMonth %in% c(4,5,6,7,8,9,10,11),
         Source!= "USGS",
         Year>2016)
```

# Look at data
A little less data in 2017, esp spring
```{r}
sampsize <- mic_data %>%
  group_by(Region, fYear, Season, fMonth) %>%
  summarize(n = n())

ggplot(sampsize) + geom_tile(aes(x = fYear, y = Season, fill = n))
ggplot(sampsize) + geom_tile(aes(x = fYear, y = fMonth, fill = n))
ggplot(sampsize) + geom_tile(aes(x = fYear, y = fMonth, fill = n)) + facet_wrap(~Region)
```

```{r}
pa <- mic_data %>%
  filter(Month %in% c(6,7,8,9,10)) %>%
  group_by(Region, fMonth, fYear) %>%
  dplyr::mutate(ntotal = n()) %>%
  ungroup() %>%
  dplyr::group_by(Region, fMonth, fYear, MicroPA, ntotal) %>%
  dplyr::summarize(n = n(),
            prop = n/ntotal)

ggplot(pa) + geom_col(aes(x = fYear, y = n, fill = MicroPA)) + 
  facet_grid(Region~fMonth, scales = "free_y") +
  scale_fill_manual(values = c("navy", "lightblue"))+
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90)) 

pa2 <- pa %>%
  dplyr::select(Region, fMonth, fYear, MicroPA, prop) %>%
  distinct()

ggplot(pa2) + geom_col(aes(x = fYear, y = prop, fill = MicroPA)) + 
  facet_grid(Region~fMonth) +
  scale_fill_manual(values = c("grey70","steelblue"))+
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90)) 
```

# Run model; check residuals

* Year filtered to Franks, Lower Sac, Lower SJ, OMR, South 
* Region filtered to 2022

## Recent Models (separate region and year)
```{r}
# filter to central and south delta
data_year <- dplyr::filter(mic_data, Region %in% c("Lower Sac", "Lower SJ","OMR", "South Delta", "Franks"), (fYear!="2017"))

datayear_sum <- data_year %>%
  group_by(fYear, fMonth) %>%
  summarize(n = n())
ggplot(datayear_sum) + geom_tile(aes(x = fYear, y = fMonth, fill = n)) + geom_text(aes(label = n, y = fMonth, x = fYear), color = "white")


datayear_sum2 <- data_year %>%
  group_by(fYear, fMonth, Source) %>%
  summarize(n = n())

pa <- data_year %>%
  group_by(fYear) %>%
  dplyr::mutate(ntotal = n()) %>%
  ungroup() %>%
  dplyr::group_by(fYear, MicroPA, ntotal) %>%
  dplyr::summarize(n = n(),
            prop = n/ntotal) %>%
  distinct() %>%
  filter(MicroPA == "1")


ggplot(datayear_sum) + geom_tile(aes(x = fYear, y = fMonth, fill = n)) + geom_text(aes(label = n, y = fMonth, x = fYear), color = "white")

# filter to 2022
data_2022 <- dplyr::filter(mic_data, fYear == "2022", !fMonth %in% c("4", "5"))

data2022_sum <- data_2022 %>%
  group_by(Region, Season) %>%
  summarize(n = n())
ggplot(data2022_sum) + geom_tile(aes(x = Region, y = Season, fill = n)) + geom_text(aes(label = n, y = Season, x = Region), color = "white")

```

```{r}
# Year only -------------------------

# glm
m0 <- glm(MicroPA ~ fYear , family = binomial(link = 'logit'), data = data_year)
summary(m0)
par(mfrow = c(2,4))
plot(m0)
resid_m0 = resid(m0, type = "pearson")
hist(resid_m0)
plot(data_year$fYear, resid_m0)

# glmer
m0a <- glmer(MicroPA ~ fYear + (1|fMonth), family = binomial, data = data_year)
summary(m0a)
anova(m0a)
plot(m0a)

par(mfrow = c(2,4))
resid0a = resid(m0a, type = "pearson")
#df1 = nuts_stats_sf %>% filter(!is.na(Nitrate), !is.na(fMonth), !is.na(Stratum2), !is.na(fYear))
lev0a = hatvalues(m0a)
plot(m0a)
qqnorm(resid0a)
qqline(resid0a)
plot(lev0a, y = resid0a)
hist(resid0a)
plot(resid0a)
plot(data_year$fYear, resid0a)
acf(resid0a)

# Region only -----------------------

# glm
mr <- glm(MicroPA ~ Region + fMonth, family = binomial(link = 'logit'), data = data_2022)
summary(mr)
par(mfrow = c(2,4))
plot(mr)
resid_mr = resid(mr, type = "pearson")
plot(data_2022$Region, resid_mr)
plot(data_2022$fMonth, resid_mr)

# random effect
ggplot()
mra <- glmer(MicroPA ~ Region + (1|Season), family = binomial, data = data_2022)
summary(mra)
plot(mra)

par(mfrow = c(2,4))
residra = resid(mra, type = "pearson")
#df1 = nuts_stats_sf %>% filter(!is.na(Nitrate), !is.na(fMonth), !is.na(Stratum2), !is.na(fYear))
lev0a = hatvalues(mra)
plot(mra)
qqnorm(residra)
qqline(residra)
plot(lev0a, y = residra)
hist(residra)
plot(residra)
plot(data_2022$Season, residra)
plot(data_2022$Region, residra)
acf(residra)


kruskal.test(MicroPA)
```






## Older models
```{r}
library(lmerTest)
library(lme4)

data_sumfall <- dplyr::filter(mic_data, !fMonth %in% c("4", "5", "11"))

# Year and Season ---------------------
m1 <- glm(MicroPA ~ fYear + Season, family=binomial(link='logit'),data=mic_data)
summary(m1)
anova(m1)

par(mfrow = c(2,4))
plot(m1)
resid_m1 = resid(m1, type = "pearson")
plot(mic_data$Region, resid_m1)
plot(mic_data$fYear, resid_m1)
plot(mic_data$Season, resid_m1)

# Year and Region -----------------
m2 <- glm(MicroPA ~ fYear + Region, family = binomial(link = 'logit'), data = data_sumfall)
summary(m2)
par(mfrow = c(2,4))
plot(m2)
resid_m2 = resid(m2, type = "pearson")
plot(data_sumfall$Region, resid_m2)
plot(data_sumfall$fYear, resid_m2)
plot(data_sumfall$fMonth, resid_m2)

m2a <- glmer(MicroPA ~ fYear + Region + (1|Season), family = binomial, data = mic_data)
summary(m2a)
plot(m2a)

par(mfrow = c(2,4))
resid2a = resid(m2a, type = "pearson")
#df1 = nuts_stats_sf %>% filter(!is.na(Nitrate), !is.na(fMonth), !is.na(Stratum2), !is.na(fYear))
lev2a = hatvalues(m2a)
plot(m2a)
qqnorm(resid2a)
qqline(resid2a)
plot(lev2a, y = resid2a)
hist(resid2a)
plot(resid2a)
plot(mic_data$fYear, resid2a)
plot(mic_data$Region, resid2a)
acf(resid2a)


# Year * Region -------------
m3 <- glm(MicroPA ~ fYear * Region, family = binomial(link = 'logit'), data = data_sumfall)
summary(m3)
par(mfrow = c(2,4))
plot(m3)
  
# this one doesn't run
m3a <- glmer(MicroPA ~ fYear * Region + (1|fMonth), family=binomial, data=data_sumfall)
summary(m3a)
anova(m3a)
```

# Look at posthoc pairwise comparisons
```{r}
library(emmeans)
confint(m1)

fit.emm <- emmeans(m1, "fYear", data=mic_data)
resultsyear <- pairs(fit.emm, adjust="tukey")
plot(fit.emm, comparisons = TRUE)
model_microcystis_year_results <- as.data.frame(resultsyear) %>%
  mutate(across(.cols = c(estimate:SE, z.ratio), ~round(.x, digits = 3))) 

fit.emm2 <- emmeans(m1, "Season", data=pa)
resultsseason <- pairs(fit.emm2, adjust="tukey")
plot(fit.emm2, comparisons = TRUE)
model_microcystis_season_results <- as.data.frame(resultsseason) %>%
  mutate(across(.cols = c(estimate:SE, z.ratio), ~round(.x, digits = 3)))
```

```{r}
confint(m2)

fit.emm <- emmeans(m2, "fYear", data=data_sumfall)
resultsyear <- pairs(fit.emm, adjust="tukey")
plot(fit.emm, comparisons = TRUE)
model_microcystis_year_results <- as.data.frame(resultsyear) %>%
  mutate(across(.cols = c(estimate:SE, z.ratio), ~round(.x, digits = 3))) 

fit.emm2 <- emmeans(m2, "Region", data=data_sumfall)
resultsregion <- pairs(fit.emm2, adjust="tukey")
plot(fit.emm2, comparisons = TRUE)
model_microcystis_region_results <- as.data.frame(resultsregion) %>%
  mutate(across(.cols = c(estimate:SE, z.ratio), ~round(.x, digits = 3)))

library(sjPlot)
plot_model(m2)
plot_model(m2a)
```


## Recent

```{r}
library(effects)
effects <- effects::effect(term = "fYear", mod = m0a)
summary(effects)

Effect(focal.predictors = "fYear", mod =  m0a)
eff.max <- allEffects(m0a, fixed.predictors = c("fYear"))
eff.max
```

```{r}
fit.emm <- emmeans(m0a, "fYear", data=data_year)
resultsyear <- pairs(fit.emm, adjust="tukey")
plot(fit.emm, comparisons = TRUE,type = "response")
(model_microcystis_year_results <- as.data.frame(resultsyear) %>%
  mutate(across(.cols = c(estimate:SE, z.ratio), ~round(.x, digits = 3))) )

confint_year <- confint(m0a)

plot_model(m0a)
(year_sj <- tab_model(m0a))

write_csv(year_sj, here("analysis_2022", "data_clean", "model_microcystis_results_sjplot_year.csv"))

fit.emm2 <- emmeans(mra, "Region", data=data_2022)
resultsregion <- pairs(fit.emm2, adjust="tukey")
plot(fit.emm2, comparisons = TRUE)
model_microcystis_region_results <- as.data.frame(resultsregion) %>%
  mutate(across(.cols = c(estimate:SE, z.ratio), ~round(.x, digits = 3)))

library(sjPlot)
plot_model(mra)

multcomp::cld(fit.emm2)
```





# Write results table to data_clean
```{r}
model_microcystis_results <- rbind(model_microcystis_year_results, model_microcystis_region_results)
write_csv(model_microcystis_results, here("analysis_2022", "data_clean", "model_microcystis_results_emmeans_year_region_sep_models.csv"))
```

