---
title: "plot_continuous_data"
author: "Catarina Pien"
date: '2022-10-08'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate) #today()
library(readr)
library(here)
library(Polychrome)
library(viridis)
library(deltamapr)
library(sf)
library(ggspatial)
library(readxl)

data_root = "analysis_2022/"
```

# Read data
```{r}
# TUCP Dates
tucp_dates <- read_excel(here("data", "tucp_dates.xlsx"))%>%
  mutate(BarrierStartDate = lubridate::ymd(BarrierStartDate),
         BarrierEndDate = ymd(BarrierEndDate),
         TUCPStart = ymd(TUCPStart),
         TUCPEnd = ymd(TUCPEnd)) %>%
  rename(WY = `Water Year`) 

# Continuous WQ
wq_data <- readRDS(here(data_root,"data_clean", "continuous_wq_2013_2022.rds")) %>%
  mutate(WY = ifelse(as.numeric(Month) >9, as.numeric(Year) + 1, as.numeric(Year)),
         fWY = factor(WY),
         fYear = factor(Year)) %>%
  filter(Year > 2014,
         Analyte !="DO.Pct",
         Date < ymd("2022-10-01"),
         !Site %in% c("BLP")) 

flow_stations <- wq_data %>% filter(Analyte == "Flow") 
unique(flow_stations$Site)

wq_data2 <- wq_data %>%
  left_join(tucp_dates) %>%
  mutate(TUCP_in_effect = case_when(TUCP == "Yes" & Date >= TUCPStart & Date <= TUCPEnd ~ "Yes",
                                    TRUE ~ "No"),
         Barrier_in_effect = case_when(Barrier == "Barrier" & Date >=BarrierStartDate & Date <=BarrierEndDate ~ "Yes",
                                       TRUE ~ "No"))%>%
  mutate(dailyval = case_when(Analyte %in% c("Temp", "Chl.a", "Turb") ~ Daily.Max,
                              Analyte == "DO.Conc" ~ Daily.Min,
                              TRUE ~ Daily.Mean),
         Date2 = paste0(1980, "-", Month, "-", day(Date)),
         Date2 = ymd(Date2)) %>%
  mutate(Region = case_when(Site %in% c("HLT", "MDM") ~ "Mildred Island",
                            Site %in% c("SJC", "SJG") ~ "San Joaquin",
                            Site == "LIB" ~ "Liberty Island",
                            Site %in% c("FAL", "HOL", "FRK", "OSJ", "ORQ", "DSJ", "FCT")~"Franks/OMR")) %>%
  mutate(TUCOComp = case_when(WY %in% c(2013, 2020)~ "DroughtNoTUCO", 
                            WY %in% c(2014, 2015, 2016, 2021)~ "DroughtTUCO", 
                            WY == 2022 ~ "2022",
                            #Year %in% c(2013, 2016, 2018, 2020) ~ "DryNoTUCO",
                            WY %in% c(2017, 2019) ~ "Wet",
                            TRUE ~ "Other"),
       EDBComp = case_when(WY %in% c(2013, 2014, 2016, 2020)~ "DroughtNoEDB",
                           WY %in% c(2015, 2021)~ "DroughtEDB",
                           #Year %in% c(2014, 2016, 2018, 2020) ~ "DryNoEDB",
                           WY == 2022 ~ "2022",
                           WY %in% c(2017, 2019) ~ "Wet",
                           TRUE ~ "Other"))
  
wq_daily_summary_Year <- wq_data2 %>%
  group_by(Region, Analyte, Date2, fYear, Year, Month) %>%
  summarize(Daily = mean(dailyval, na.rm = TRUE))

wq_data_summary_TUCO <- wq_data2 %>%
  group_by(TUCOComp, Month, Region, Analyte, Date2) %>%
  summarize(Daily = mean(dailyval, na.rm = TRUE))

wq_data_summary_EDB <- wq_data2 %>%
  group_by(EDBComp,  Month,Region, Analyte, Date2) %>%
  summarize(Daily = mean(dailyval, na.rm = TRUE))
  


# Make individuals
wq_frk <- wq_data2 %>% filter(Region == "Franks/OMR")

wq_mil <- wq_data2 %>% filter(Region == "Mildred Island")

wq_sj <-  wq_data2 %>% filter(Region == "San Joaquin")

wq_lib <- wq_data2 %>% filter(Region == "Liberty Island")

# Mean across stations: 
# Maximum temperature, chla, turb
# Minimum DO
# Mean Flow, pH, SpCnd


# Filter down to dry years and get mean as determined above across stations
daily_frk0 <- wq_frk %>%
  filter(fYear %in% c("2015", "2020", "2021", "2022")) %>%
  group_by(Date, Date2, Year, Julian, Month, fYear, Analyte, TUCP_in_effect, TUCP, Barrier_in_effect, Barrier) %>%
  summarize(Daily = mean(dailyval, na.rm = TRUE)) %>%
  filter(!is.na(Date)) %>%
  mutate(Location = "Frank's Tract")

daily_mil0 <- wq_mil %>%
  filter(fYear %in% c("2015", "2020", "2021", "2022")) %>%
  group_by(Date, Date2, Year, WaterYear, Julian, Month, fYear, Analyte, TUCP_in_effect, TUCP, Barrier_in_effect, Barrier) %>%
  summarize(Daily = mean(dailyval, na.rm = TRUE)) %>%
  filter(!is.na(Date))%>%
  mutate(Location = "Mildred Island")

daily_lib0 <- wq_lib %>%
filter(fYear %in% c("2015", "2020", "2021", "2022")) %>%
  group_by(Date, Date2, Year, WaterYear, Julian, Month, fYear, Analyte, TUCP_in_effect, TUCP, Barrier_in_effect, Barrier) %>%
  summarize(Daily = mean(dailyval, na.rm = TRUE)) %>%
  filter(!is.na(Date))%>%
  mutate(Location = "Liberty Island")

wq_summaryf <- daily_frk0 %>%
  group_by(Analyte) %>%
  summarize(max = max(Daily))
wq_summarym <- daily_mil0 %>%
  group_by(Analyte) %>%
  summarize(max = max(Daily))
wq_summaryl <- daily_lib0 %>%
  group_by(Analyte) %>%
  summarize(max = max(Daily))

wq_summary_all <- rbind(wq_summaryf, wq_summarym, wq_summaryl) %>%
  group_by(Analyte) %>%
  summarize(max = max(max))

wq_summary <- wq_data2 %>%
  group_by(Analyte, TUCPStart, TUCPEnd, BarrierStartDate, BarrierEndDate) %>%
  filter(!is.na(TUCPStart)) %>%
  summarize(max = max(dailyval),
            max2 = Inf,
            min2 = -Inf)

daily_frk <- left_join(daily_frk0, wq_summary_all) %>%
  mutate(TUCP_value = ifelse(TUCP_in_effect == "Yes", max, 0),
         Barrier_value = ifelse(Barrier_in_effect == "Yes", max, 0))
daily_mil <- left_join(daily_mil0, wq_summary_all) %>%
  mutate(TUCP_value = ifelse(TUCP_in_effect == "Yes", max, 0),
         Barrier_value = ifelse(Barrier_in_effect == "Yes", max, 0))
daily_lib <- left_join(daily_lib0, wq_summary_all) %>%
  mutate(TUCP_value = ifelse(TUCP_in_effect == "Yes", max, 0),
         Barrier_value = ifelse(Barrier_in_effect == "Yes", max, 0))
```

```{r}
frk_wq_stats <- daily_frk %>%
  group_by(Year, Analyte) %>%
  summarize(mean = mean(Daily),
            min = min(Daily),
            max = max(Daily))
```


# NEW

## WQ
Dataframe without flow, velocity, san joaquin region
```{r}
# 2022 data
unique(wq_data2$Region)
wq_a <- wq_data2 %>% 
  filter(Analyte != "Flow",
         Analyte != "Velocity",
         !Region %in% c("Liberty Island", "San Joaquin")) 

wq_summary2022 <- wq_a %>%
  dplyr::select(-Date2) %>%
  filter(!is.na(TUCPStart),
         Year == 2022) %>%
  group_by(Analyte, TUCPStart, TUCPEnd, BarrierStartDate, BarrierEndDate) %>%
  summarize(max = max(dailyval)) %>%
  ungroup()

wq_2022 <- wq_a %>%
  filter(!Month %in% c("Jan", "Feb", "Nov", "Dec"),
         Year == 2022)

# All years 
wq_yearcomp <- wq_a %>%
  filter(Year %in% c(2015, 2016,2020, 2021, 2022))  %>%
  ungroup() %>%
  droplevels()

wq_yearcomp <- subset(wq_yearcomp, Year%in% c(2015, 2016, 2020, 2021, 2022))





wq_EDB <- wq_data_summary_EDB %>%
  filter(!Region %in% c("San Joaquin", "Liberty Island"),
         !Analyte %in% c("Flow", "Velocity"),
         !EDBComp %in% c("Other", "Wet"),
         !Month %in% c("Nov", "Dec"))


```

### 2022 
Individual stations - 2022
```{r}
templine <- data.frame(Analyte = c("Temp"), int = c(19))

(plot_cont_2022 <- ggplot() +
    # shaded box
    geom_rect(data = 
                data.frame(xmin = ymd(wq_summary2022$TUCPStart), 
                           xmax = ymd(wq_summary2022$TUCPEnd), 
                           ymin = -Inf, ymax = Inf),
                aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
                fill = "gray95", alpha = 0.5) +
    # line for temperature at 19
    geom_hline(data = templine, aes(yintercept = int)) + 
    geom_vline(xintercept = date("2022-04-15"), linetype = "dotted") +
    geom_vline(xintercept = date("2022-11-02"), linetype = "dotted") +
    # WQ data
    geom_line(data= wq_2022, aes(x = Date, y = dailyval, color = Site, linetype = Region), 
              inherit.aes = FALSE) + 
    # facet all the panels
    facet_wrap(~Analyte, scales = "free_y", nrow = 6, strip.position = "left", 
             labeller = as_labeller(c(Chl.a = "Chl a\n(mg/L)",DO.Conc = "DO \n(mg/L)", 
            #Flow = "Flow (cfs)", 
    pH = "pH",SpCond="SpCnd \n(mS/cm)", Turb="Turbidity \n(FNU)", Temp="Water Temp \n(°C)")))+
    
    theme(strip.background = element_rect(fill="White", color = "White"),
          strip.placement = "outside", axis.title.y = element_blank(), legend.position = "top")+
    scale_color_viridis(option = "turbo", discrete = TRUE) +
    scale_x_date(breaks = "month", date_labels = "%b", expand = c(0,0)) + 
    scale_linetype_manual(values = c("dashed", "solid", "dotted")) +
    labs(y = "Daily Mean Value") +
    theme_bw() +
    theme(strip.text = element_text(size = 12),
          axis.text = element_text(size = 12),
          axis.title.x = element_blank(),
          legend.text = element_text(size = 12),
          legend.title = element_text(size = 12),
          legend.position = "top",
          legend.box = "vertical"))
```

### Across years
```{r}

analytes <- data.frame(Analyte = rep(unique(wq_yearcomp$Analyte),5),
                       fYear = c(rep("2015", 6), rep("2016", 6), rep("2020", 6), rep("2021", 6), rep("2022", 6)))

tucp.df <- tucp_dates %>%
  mutate(fYear = factor(WY)) %>%
  filter(fYear %in% c("2015", "2016", "2020", "2021", "2022")) %>%
  select(fYear, TUCPStart, TUCPEnd, BarrierStartDate, BarrierEndDate) %>%
  left_join(analytes) %>%
  mutate(xmin = ymd(paste0("1980-", lubridate::month(TUCPStart),"-", day(TUCPStart))), 
         xmax = ymd(paste0("1980-", lubridate::month(TUCPEnd), "-",day(TUCPEnd))), 
         ymin = -Inf, 
         ymax = Inf,
         EDBStart = ymd(paste0("1980-", month(BarrierStartDate),"-", day(BarrierStartDate))),
         EDBEnd = ymd(paste0("1980-",month(BarrierEndDate), "-",day(BarrierEndDate))),
         EDBEnd = ifelse(fYear == "2021", NA, EDBEnd)) %>%
  mutate(fYear = factor(fYear))

str(tucp.df)
str(wq_yearcomp)
```

```{r}
# Frank's and Mildred Island
(plot_cont_jday <- ggplot() +
   geom_rect(data = tucp.df,
             aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill = "gray", alpha = 0.3) + 
  geom_line(data = wq_yearcomp, aes(x = Date2, y = dailyval, color = Site, linetype = Region)) + 
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
   # line for temperature at 19
    geom_hline(data = templine, aes(yintercept = int)) + 
   geom_vline(data = tucp.df, aes(xintercept = EDBStart), linetype = "dotted") +
   geom_vline(data = tucp.df, aes(xintercept = EDBEnd), linetype = "dotted") + 
  facet_grid(Analyte~fYear, scales = "free_y",  labeller = as_labeller(c(
    `2016` = "2016", `2015` = "2015 (E/T)", `2020` = "2020", `2021` = "2021 (E/T)", `2022` = "2022 (E/T)",
    Chl.a = "Chl a\n(mg/L)",DO.Conc = "DO \n(mg/L)",                                                          pH = "pH",SpCond="SpCnd \n(mS/cm)", Turb="Turbidity \n(FNU)", Temp="Water Temp \n(°C)")))+
    theme(strip.background = element_rect(fill="White", color = "White"),
          strip.placement = "outside", axis.title.y = element_blank(), legend.position = "top")+
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "2 months", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Daily Mean Value", color = "Station") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
         axis.title.x = element_blank(),
         legend.text = element_text(size = 12),
         legend.title = element_text(size = 12),
         legend.position = "top",
         legend.box = "vertical"))
```

#### Write
```{r}
png(filename = here("analysis_2022", "figures", "plot_wq_years.png"), width = 8, height = 8.5, units = "in", pointsize = 12, family = "sans", res = 300)
plot_cont_jday
dev.off()
```


### Frk vs MI - EDB
```{r}
(plot_mil_vs_frk <- ggplot(wq_EDB) +
 # geom_point(aes(x = Date2, y = TUCP_value), fill = "gray87", color = "gray87") + 
 # geom_col(aes(x = Date2, y = Barrier_value), fill = "bisque", color = "bisque", alpha = 0.3) + 
  geom_line(aes(x = Date2, y = Daily, color = Region)) + 
    #geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  facet_grid(Analyte~EDBComp, scales = "free_y", 
             labeller = as_labeller(c(`DroughtEDB` = "EDB Drought Year", `DroughtNoEDB` = "No EDB Drought Year", `2022` = "2022", Chl.a = "Chl a\n(mg/L)",DO.Conc = "DO \n(mg/L)", 
                                      #Flow = "Flow (cfs)", 
                                      pH = "pH",SpCond="SpCnd \n(mS/cm)", Turb="Turbidity \n(FNU)", Temp="Water \nTemp \n(°C)"))) +
  scale_color_brewer(palette = "Set1") +
   scale_x_date(breaks = "2 months", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Daily Mean Value", color = "Location") + 
    scale_y_continuous(expand = c(0,0))+
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         legend.text = element_text(size = 12),
         legend.title = element_text(size = 12),
         legend.position = "top"))
```

```{r}
(plot_mil_vs_frk <- ggplot(wq_EDB) +
 # geom_point(aes(x = Date2, y = TUCP_value), fill = "gray87", color = "gray87") + 
 # geom_col(aes(x = Date2, y = Barrier_value), fill = "bisque", color = "bisque", alpha = 0.3) + 
  geom_line(aes(x = Date2, y = Daily, color = Region)) + 
    #geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  facet_grid(Analyte~EDBComp, scales = "free_y", 
             labeller = as_labeller(c(`DroughtEDB` = "EDB Drought Year", `DroughtNoEDB` = "No EDB Drought Year", `2022` = "2022", Chl.a = "Chl a\n(mg/L)",DO.Conc = "DO \n(mg/L)", 
                                      #Flow = "Flow (cfs)", 
                                      pH = "pH",SpCond="SpCnd \n(mS/cm)", Turb="Turbidity \n(FNU)", Temp="Water \nTemp \n(°C)"))) +
  scale_color_brewer(palette = "Set1") +
   scale_x_date(breaks = "2 months", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Daily Mean Value", color = "Location") + 
    scale_y_continuous(expand = c(0,0))+
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         legend.text = element_text(size = 12),
         legend.title = element_text(size = 12),
         legend.position = "top"))
```

```{r}

```


## Flow
```{r}
flow_daily <- wq_daily_summary_Year %>%
  filter(Region!= "San Joaquin",
         Analyte == "Flow")

flow_daily_EDB <- wq_data_summary_EDB%>%
  filter(Region!= "San Joaquin",
         Analyte == "Flow",
         Month != "Jan",
         Month!="Feb",
         EDBComp %in% c("2022", "DroughtEDB", "DroughtNoEDB"))

flow_daily_TUCO <- wq_data_summary_TUCO%>%
  filter(Region!= "San Joaquin",
         Analyte == "Flow",
         Month != "Jan",
         Month!="Feb",
         TUCOComp %in% c("2022", "DroughtTUCO", "DroughtNoTUCO"))
```

```{r}
flow_2022 <- wq_data2 %>%
  filter(Year == "2022") %>%
  filter(Region!="San Joaquin",
         Analyte == "Flow") %>%

  select(-Date2) %>%
    group_by(Site, Date, Month, Region) %>%
  summarize(Daily = max(dailyval))
```


## Plot
```{r}
(plot_flow_edb <- ggplot(flow_daily_EDB) +
  geom_line(aes(x = Date2, y = Daily, color = EDBComp)) + 
  facet_wrap(~Region, nrow = 3, scales = "free_y") + 
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Flow (cfs)", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top"))
```


```{r}
(plot_flow_tuco <- ggplot(flow_daily_TUCO) +
  geom_line(aes(x = Date2, y = Daily, color = TUCOComp)) + 
  facet_wrap(~Region, nrow = 3, scales = "free_y") + 
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Flow (cfs)", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top"))
```

```{r}
png(filename = here("analysis_2022", "figures", "plot_flow_tuco.png"), width = 5, height = 4, units = "in", pointsize = 12, family = "sans", res = 300)
plot_flow_tuco
dev.off()


png(filename = here("analysis_2022", "figures", "plot_flow_edb.png"), width = 5, height = 4, units = "in", pointsize = 12, family = "sans", res = 300)
plot_flow_edb
dev.off()
```


```{r}
(plot_flow <- ggplot(flow_daily %>% filter(!Month%in% c("Jan", "Feb", "Nov", "Dec"))) +
  geom_line(aes(x = Date2, y = Daily, color = fYear)) + 
  facet_grid(fYear~Region) + 
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Flow (cfs)", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top"))
```

```{r}
(plot_flow_2022 <- ggplot(flow_2022 %>% filter(!Month%in% c("Jan", "Feb", "Nov", "Dec", "Oct"))) +
    geom_rect(data = 
                data.frame(xmin = ymd(wq_summary2022$TUCPStart), 
                           xmax = ymd(wq_summary2022$TUCPEnd), 
                           ymin = -Inf, ymax = Inf),
               aes(xmin = xmin, 
                   xmax = xmax, 
                   ymin = ymin, 
                   ymax = ymax),
                fill = "gray95", alpha = 0.5) +
     geom_rect(data = 
                data.frame(xmin = ymd(wq_summary2022$BarrierStartDate), 
                           xmax = ymd(wq_summary2022$BarrierEndDate), 
                           ymin = -Inf, ymax = Inf),
               aes(xmin = xmin, 
                   xmax = xmax, 
                   ymin = ymin, 
                   ymax = ymax),
                fill = "azure1", alpha = 0.05) +
   geom_line(aes(x = Date, y = Daily, color = Site)) + 
   facet_wrap(~Region, nrow = 3) + 
   
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Flow (cfs)", color = "Station") +  
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top",
         legend.box = "vertical"))
```

## Table

```{r}
table_flow <- flow_daily %>%
  filter(fYear == "2022") %>%
  filter(!Month %in% c("Jan", "Nov", "Dec", "Feb")) %>%
  group_by(Region, Month) %>%
  summarize(Min_Outflow = round(min(Daily),2),
            Max_Outflow = round(max(Daily),2),
            Mean_Outflow = round(mean(Daily),2),
            SD_Outflow = round(sd(Daily)),2) %>%
  ungroup() %>%
  pivot_wider(names_from = "Region", values_from = c("Min_Outflow", "Max_Outflow", "Mean_Outflow", "SD_Outflow"), id_cols = "Month")

write_csv(table_flow, "analysis_2022/data_clean/table_deltaflows.csv")
```

## Velocity
```{r}
vel_daily <- wq_daily_summary_Year %>%
  filter(Region!= "San Joaquin",
         Analyte == "Velocity")

vel_daily_EDB <- wq_data_summary_EDB%>%
  filter(Region!= "San Joaquin",
         Analyte == "Velocity",
         Month != "Jan",
         Month!="Feb",
         EDBComp %in% c("2022", "DroughtEDB", "DroughtNoEDB"))

vel_daily_TUCO <- wq_data_summary_TUCO%>%
  filter(Region!= "San Joaquin",
         Analyte == "Velocity",
         Month != "Jan",
         Month!="Feb",
         TUCOComp %in% c("2022", "DroughtTUCO", "DroughtNoTUCO"))
```

```{r}
vel_2022 <- wq_data2 %>%
  filter(Year == "2022") %>%
  filter(Region!="San Joaquin",
         Analyte == "Velocity") %>%

  select(-Date2) %>%
    group_by(Site, Date, Month, Region) %>%
  summarize(Daily = max(dailyval))
```


## Plot
```{r}
(plot_vel_edb <- ggplot(vel_daily_EDB) +
  geom_line(aes(x = Date2, y = Daily, color = EDBComp)) + 
  facet_wrap(~Region, nrow = 3, scales = "free_y") + 
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Velocity", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top"))
```


```{r}
(plot_vel_tuco <- ggplot(vel_daily_TUCO) +
  geom_line(aes(x = Date2, y = Daily, color = TUCOComp)) + 
  facet_wrap(~Region, nrow = 3, scales = "free_y") + 
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Velocity (cfs)", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top"))
```

```{r}
png(filename = here("analysis_2022", "figures", "plot_vel_tuco.png"), width = 5, height = 4, units = "in", pointsize = 12, family = "sans", res = 300)
plot_vel_tuco
dev.off()


png(filename = here("analysis_2022", "figures", "plot_vel_edb.png"), width = 5, height = 4, units = "in", pointsize = 12, family = "sans", res = 300)
plot_vel_edb
dev.off()
```


```{r}
(plot_vel <- ggplot(vel_daily %>% filter(!Month%in% c("Jan", "Feb", "Nov", "Dec"))) +
  geom_line(aes(x = Date2, y = Daily, color = fYear)) + 
  facet_grid(fYear~Region) + 
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Flow (cfs)", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top"))
```

```{r}
(plot_vel_2022 <- ggplot(vel_2022 %>% filter(!Month%in% c("Jan", "Feb", "Nov", "Dec", "Oct"))) +
    geom_rect(data = 
                data.frame(xmin = ymd(wq_summary2022$TUCPStart), 
                           xmax = ymd(wq_summary2022$TUCPEnd), 
                           ymin = -Inf, ymax = Inf),
               aes(xmin = xmin, 
                   xmax = xmax, 
                   ymin = ymin, 
                   ymax = ymax),
                fill = "gray95", alpha = 0.5) +
     geom_rect(data = 
                data.frame(xmin = ymd(wq_summary2022$BarrierStartDate), 
                           xmax = ymd(wq_summary2022$BarrierEndDate), 
                           ymin = -Inf, ymax = Inf),
               aes(xmin = xmin, 
                   xmax = xmax, 
                   ymin = ymin, 
                   ymax = ymax),
                fill = "azure1", alpha = 0.05) +
   geom_line(aes(x = Date, y = Daily, color = Site)) + 
   facet_wrap(~Region, nrow = 3) + 
   
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Velocity (cfs)", color = "Station") +  
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top",
         legend.box = "vertical"))
```

```{r}
png(filename = here("analysis_2022", "figures", "plot_vel_tuco.png"), width = 5, height = 4, units = "in", pointsize = 12, family = "sans", res = 300)
plot_vel_tuco
dev.off()


png(filename = here("analysis_2022", "figures", "plot_vel_edb.png"), width = 5, height = 4, units = "in", pointsize = 12, family = "sans", res = 300)
plot_vel_edb
dev.off()


png(filename = here("analysis_2022", "figures", "plot_velocity_2022.png"), width = 5, height = 4, units = "in", pointsize = 12, family = "sans", res = 300)
plot_vel_2022
dev.off()
```










# Velocity
```{r}
vel_daily_frk <- filter(daily_frk, Analyte== "Velocity")
vel_daily_mil <- filter(daily_mil, Analyte== "Velocity")
vel_daily_lib <- filter(daily_lib, Analyte== "Velocity")
vel_daily <- rbind(vel_daily_frk, vel_daily_mil, vel_daily_lib)
vel_2022 <- wq_data2 %>%
  filter(Year == "2022",
         Analyte == "Velocity") %>%
  mutate(Location = ifelse(Site %in% c("MDM", "HLT"), "Mildred Island", 
                           ifelse(Site %in% c("SJC", "SJG"), "San Joaquin",
                                  ifelse(Site == "LIB", "Liberty Island",
                           "Frank's Tract")))) %>%
  select(-Date2) %>%
  filter(Location != "San Joaquin")
```

## Plot
```{r}
(plot_vel <- ggplot(vel_daily %>% filter(!Month%in% c("Jan", "Feb", "Nov", "Dec"))) +
   geom_line(aes(x = Date2, y = Daily, color = fYear)) + 
   
    facet_wrap(~Location, nrow = 3) + 
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Velocity (ft/s)", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top"))
```


```{r}
(plot_velocity_2022 <- ggplot(vel_2022 %>% filter(!Month%in% c("Jan", "Feb", "Nov", "Dec"))) +
    geom_rect(data = 
                data.frame(xmin = ymd(wq_summary2022$TUCPStart), 
                           xmax = ymd(wq_summary2022$TUCPEnd), 
                           ymin = -Inf, ymax = Inf),
               aes(xmin = xmin, 
                   xmax = xmax, 
                   ymin = ymin, 
                   ymax = ymax),
                fill = "gray95", alpha = 0.5) +
    geom_rect(data = 
                data.frame(xmin = ymd(wq_summary2022$BarrierStartDate), 
                           xmax = ymd(wq_summary2022$BarrierEndDate), 
                           ymin = -Inf, ymax = Inf),
               aes(xmin = xmin, 
                   xmax = xmax, 
                   ymin = ymin, 
                   ymax = ymax),
                fill = "bisque3", alpha = 0.05) +
   geom_line(aes(x = Date, y = dailyval, color = Site, linetype = Location)) + 
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Velocity (ft/s)", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top",
         legend.box = "vertical"))
```















# WQ

WQ
```{r}
wq_daily_frk <- filter(daily_frk, Analyte!= "Flow", Analyte!= "Velocity")
wq_daily_mil <- filter(daily_mil, Analyte!= "Flow", Analyte!= "Velocity")
wq_daily_lib <- filter(daily_lib, Analyte!= "Flow", Analyte!= "Velocity")
```


## 2022 only
```{r}
wq_2022_a <- wq_data2 %>% dplyr::select(-Date2) %>%
  filter(Year == 2022,
         Analyte != "Flow",
         Analyte != "Velocity") 

wq_summary2022 <- wq_2022_a %>%
  group_by(Analyte, TUCPStart, TUCPEnd, BarrierStartDate, BarrierEndDate) %>%
  filter(!is.na(TUCPStart)) %>%
  summarize(max = max(dailyval))

wq_2022 <- left_join(wq_2022_a, wq_summary2022)%>%
  mutate(TUCP_value = ifelse(TUCP_in_effect == "Yes", max, 0))

templine <- data.frame(Analyte = c("Temp"), int = c(19))

(plot_cont_2022 <- ggplot() +
    # shaded box
    geom_rect(data = 
                data.frame(xmin = ymd(wq_summary2022$TUCPStart), 
                           xmax = ymd(wq_summary2022$TUCPEnd), 
                           ymin = -Inf, ymax = Inf),
                aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
                fill = "gray95", alpha = 0.5) +
    # line for temperature at 19
    geom_hline(data = templine, aes(yintercept = int)) + 
    # WQ data
    geom_line(data= wq_2022, aes(x = Date, y = dailyval, color = Site, linetype = Location), 
              inherit.aes = FALSE) + 
    # facet all the panels
    facet_wrap(~Analyte, scales = "free_y", nrow = 6, strip.position = "left", 
             labeller = as_labeller(c(Chl.a = "Chl a\n(mg/L)",DO.Conc = "DO \n(mg/L)", 
            #Flow = "Flow (cfs)", 
    pH = "pH",SpCond="SpCnd \n(mS/cm)", Turb="Turbidity \n(FNU)", Temp="Water Temp \n(°C)")))+
    
    theme(strip.background = element_rect(fill="White", color = "White"),
          strip.placement = "outside", axis.title.y = element_blank(), legend.position = "top")+
    scale_color_viridis(option = "turbo", discrete = TRUE) +
    scale_x_date(breaks = "month", date_labels = "%b", expand = c(0,0)) + 
    scale_linetype_manual(values = c("dashed", "solid")) +
    labs(y = "Daily Mean Value") +
    theme_bw() +
    theme(strip.text = element_text(size = 12),
          axis.text = element_text(size = 12),
          axis.title.x = element_blank(),
          legend.text = element_text(size = 12),
          legend.title = element_text(size = 12),
          legend.position = "top",
          legend.box = "vertical"))
```

When did temps>19 start?
```{r}
temp <- wq_2022 %>% filter(Analyte == "Temp") %>% 
    select(Site, Year, Month, Date, Daily.Max) %>%
  mutate(HOT = ifelse(Daily.Max > 19, 1,0),
         daysrow = HOT + lag(HOT))


temp_hot <- temp %>% 
  filter(HOT == "Y") %>%
  group_by(Site) %>%
  summarize(n = n(),
            firstDate = first(Date),
            lastDate = last(Date))

# April in Frank's Tract, April 7 in Mildred Island
# Consistent: May 17 (FAL), May 13-15 for all other sites

```

## Across year, by parameter - don't use this plot
```{r}
(plot_cont_allyears <- ggplot(wq_data) + 
   geom_line(aes(x = Date, y = Daily.Mean, color = Site)) + 
  facet_wrap(~Analyte, scales = "free_y", nrow = 8, strip.position = "left", labeller = as_labeller(c(Chl.a = "Chl a\n(mg/L)",DO.Conc = "DO \n(mg/L)", Flow = "Flow (cfs)", pH = "pH",SpCond="SpCnd \n(mS/cm)", Turb="Turbidity \n(FNU)", Temp="Water Temp \n(°C)")))+
    theme(strip.background = element_rect(fill="White", color = "White"),
          strip.placement = "outside", axis.title.y = element_blank(), legend.position = "top")+
  scale_color_viridis(option = "turbo", discrete = TRUE) +
  scale_x_date(breaks = "3 months", date_labels = "%b", expand = c(0,0))+ 
  labs(y = "Daily Mean Value") + 
  theme_bw())
```

## View by year
```{r}
# Frank's Tract
(plot_cont_jday_frk <- ggplot(wq_daily_frk) +
  geom_line(aes(x = Date2, y = Daily, color = fYear)) + 
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  facet_wrap(~Analyte, scales = "free_y", nrow = 6, strip.position = "left", labeller = as_labeller(c(Chl.a = "Chl a\n(mg/L)",DO.Conc = "DO \n(mg/L)", 
                                                                                                      #Flow = "Flow (cfs)", 
                                                                                                      pH = "pH",SpCond="SpCnd \n(mS/cm)", Turb="Turbidity \n(FNU)", Temp="Water Temp \n(°C)")))+
    theme(strip.background = element_rect(fill="White", color = "White"),
          strip.placement = "outside", axis.title.y = element_blank(), legend.position = "top")+
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Daily Mean Value", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         legend.text = element_text(size = 12),
         legend.title = element_text(size = 12),
         legend.position = "top"))

# Mildred Island
(plot_cont_jday_mil <- ggplot(wq_daily_mil) +
  geom_line(aes(x = Date2, y = Daily, color = fYear)) + 
    #geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  facet_wrap(~Analyte, scales = "free_y", nrow = 8, strip.position = "left", labeller = as_labeller(c(Chl.a = "Chl a\n(mg/L)",DO.Conc = "DO \n(mg/L)", DO.Pct = "DO %",Flow = "Flow (cfs)", pH = "pH",SpCond="SpCnd \n(mS/cm)", Turb="Turbidity \n(FNU)", Temp="Water Temp \n(°C)")))+
    theme(strip.background = element_rect(fill="White", color = "White"),
          strip.placement = "outside", axis.title.y = element_blank(), legend.position = "top")+
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Daily Mean Value", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         legend.text = element_text(size = 12),
         legend.title = element_text(size = 12),
         legend.position = "top"))
```

Comparing Mildred Island and Frank's Tract, select years
```{r}
wq_daily_comb <- rbind(wq_daily_mil, wq_daily_frk) %>%
  filter(fYear %in% c("2015", "2020", "2021", "2022"))

# df <- data.frame(xmin = ymd(wq_summary$BarrierStartDate), 
#                            xmax = ymd(wq_summary2022$BarrierEndDate), 
#                            ymin = -Inf, ymax = Inf)
# 
# 
#                aes(xmin = xmin, 
#                    xmax = xmax, 
#                    ymin = ymin, 
#                    ymax = ymax),
#                 fill = "bisque3", alpha = 0.05) 



(plot_mil_vs_frk <- ggplot(wq_daily_comb) +
  geom_point(aes(x = Date2, y = TUCP_value), fill = "gray87", color = "gray87") + 
  geom_col(aes(x = Date2, y = Barrier_value), fill = "bisque", color = "bisque", alpha = 0.3) + 
  geom_line(aes(x = Date2, y = Daily, color = Location)) + 
    #geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  facet_grid(Analyte~fYear, scales = "free_y", 
             labeller = as_labeller(c(`2015` = "2015", `2020` = "2020 (no TUCP)", `2021` = "2021", `2022` = "2022", Chl.a = "Chl a\n(mg/L)",DO.Conc = "DO \n(mg/L)", 
                                      #Flow = "Flow (cfs)", 
                                      pH = "pH",SpCond="SpCnd \n(mS/cm)", Turb="Turbidity \n(FNU)", Temp="Water \nTemp \n(°C)"))) +
  scale_color_brewer(palette = "Set1") +
   scale_x_date(breaks = "2 months", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Daily Mean Value", color = "Location") + 
    scale_y_continuous(expand = c(0,0))+
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         legend.text = element_text(size = 12),
         legend.title = element_text(size = 12),
         legend.position = "top"))
```

# Salinity
```{r}
spc <- readRDS(here(data_root, "data_raw", "CDEC_spc_EMM_TMS_2013_2022.rds")) %>%
  mutate(Date2 = paste0(1980, "-", Month, "-", day(Date)),
         Date2 = ymd(Date2))
spc_dry <- filter(spc, Year %in% c(2013, 2016, 2020, 2022),
                  !Month %in% c("Jan", "Feb", "Nov", "Dec"))

table <- spc_dry %>%
  mutate(Group = ifelse(Year == 2022, "2022", "Other")) %>%
  group_by(Group, Site, Month) %>%
  summarize(mean = mean(Daily.Mean))
```

```{r}
(plot_spc<-ggplot() + 
  geom_rect(data = 
                data.frame(xmin = lubridate::ymd("1980-04-01"), 
                           xmax = lubridate::ymd("1980-06-30"), 
                           ymin = -Inf, ymax = Inf),
               aes(xmin = xmin, 
                   xmax = xmax, 
                   ymin = ymin, 
                   ymax = ymax),
                fill = "gray95", alpha = 0.5) +
  geom_line(data = spc_dry, aes(x = Date2, y= Daily.Mean, color = factor(Year))) + 
  scale_color_viridis(discrete = TRUE, option = "turbo") + 
   
  facet_wrap(~factor(Site), nrow = 2) +
  labs(y = "Daily Mean SPCond (uS/cm)") + 
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + theme_bw() +
  theme(axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = "top"))
```

Write plot
```{r}
png(filename = here("analysis_2022", "figures", "plot_spc.png"), width = 6, height = 4, units = "in", pointsize = 12, family = "sans", res = 300)
plot_spc
dev.off()
```



# Flow

```{r}
flow_daily_frk <- filter(daily_frk, Analyte== "Flow")
flow_daily_mil <- filter(daily_mil, Analyte== "Flow")
flow_daily_lib <- filter(daily_lib, Analyte == "Flow")
flow_daily <- rbind(flow_daily_frk, flow_daily_mil, flow_daily_lib)

flow_2022 <- wq_data2 %>%
  filter(Year == "2022",
         Analyte == "Flow") %>%
  mutate(Location = ifelse(Site %in% c("MDM", "HLT"), "Mildred Island", 
                           ifelse(Site %in% c("SJC", "SJG"), "San Joaquin",
                                  ifelse(Site == "LIB", "Liberty Island",
                           "Frank's Tract")))) %>%
  select(-Date2) %>%
  filter(Location != "San Joaquin")
```


## Plot
```{r}
(plot_flow <- ggplot(flow_daily %>% filter(!Month%in% c("Jan", "Feb", "Nov", "Dec"))) +
   geom_line(aes(x = Date2, y = Daily, color = fYear)) + 
   
    facet_wrap(~Location, nrow = 3) + 
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Flow (cfs)", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top"))
```

```{r}
(plot_flow_2022 <- ggplot(flow_2022 %>% filter(!Month%in% c("Jan", "Feb", "Nov", "Dec"))) +
    geom_rect(data = 
                data.frame(xmin = ymd(wq_summary2022$TUCPStart), 
                           xmax = ymd(wq_summary2022$TUCPEnd), 
                           ymin = -Inf, ymax = Inf),
               aes(xmin = xmin, 
                   xmax = xmax, 
                   ymin = ymin, 
                   ymax = ymax),
                fill = "gray95", alpha = 0.5) +
     geom_rect(data = 
                data.frame(xmin = ymd(wq_summary2022$BarrierStartDate), 
                           xmax = ymd(wq_summary2022$BarrierEndDate), 
                           ymin = -Inf, ymax = Inf),
               aes(xmin = xmin, 
                   xmax = xmax, 
                   ymin = ymin, 
                   ymax = ymax),
                fill = "bisque3", alpha = 0.05) +
   geom_line(aes(x = Date, y = dailyval, color = Site, linetype = Location)) + 
   
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
   scale_linetype_manual(values = c("solid", "dotdash", "longdash")) + 
  labs(y = "Flow (cfs)", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top",
         legend.box = "vertical"))
```



## Table

```{r}
table_flow <- flow_daily %>%
  filter(fYear == "2022") %>%
  filter(!Month %in% c("Jan", "Nov", "Dec", "Feb")) %>%
  group_by(Location, Month) %>%
  summarize(Min_Outflow = round(min(Daily),2),
            Max_Outflow = round(max(Daily),2),
            Mean_Outflow = round(mean(Daily),2),
            SD_Outflow = round(sd(Daily)),2) %>%
  ungroup() %>%
  pivot_wider(names_from = "Location", values_from = c("Min_Outflow", "Max_Outflow", "Mean_Outflow", "SD_Outflow"), id_cols = "Month")

write_csv(table_flow, "analysis_2022/data_clean/table_deltaflows.csv")
```




# Velocity
```{r}
vel_daily_frk <- filter(daily_frk, Analyte== "Velocity")
vel_daily_mil <- filter(daily_mil, Analyte== "Velocity")
vel_daily_lib <- filter(daily_lib, Analyte== "Velocity")
vel_daily <- rbind(vel_daily_frk, vel_daily_mil, vel_daily_lib)
vel_2022 <- wq_data2 %>%
  filter(Year == "2022",
         Analyte == "Velocity") %>%
  mutate(Location = ifelse(Site %in% c("MDM", "HLT"), "Mildred Island", 
                           ifelse(Site %in% c("SJC", "SJG"), "San Joaquin",
                                  ifelse(Site == "LIB", "Liberty Island",
                           "Frank's Tract")))) %>%
  select(-Date2) %>%
  filter(Location != "San Joaquin")
```

## Plot
```{r}
(plot_vel <- ggplot(vel_daily %>% filter(!Month%in% c("Jan", "Feb", "Nov", "Dec"))) +
   geom_line(aes(x = Date2, y = Daily, color = fYear)) + 
   
    facet_wrap(~Location, nrow = 3) + 
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Velocity (ft/s)", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top"))
```


```{r}
(plot_velocity_2022 <- ggplot(vel_2022 %>% filter(!Month%in% c("Jan", "Feb", "Nov", "Dec"))) +
    geom_rect(data = 
                data.frame(xmin = ymd(wq_summary2022$TUCPStart), 
                           xmax = ymd(wq_summary2022$TUCPEnd), 
                           ymin = -Inf, ymax = Inf),
               aes(xmin = xmin, 
                   xmax = xmax, 
                   ymin = ymin, 
                   ymax = ymax),
                fill = "gray95", alpha = 0.5) +
    geom_rect(data = 
                data.frame(xmin = ymd(wq_summary2022$BarrierStartDate), 
                           xmax = ymd(wq_summary2022$BarrierEndDate), 
                           ymin = -Inf, ymax = Inf),
               aes(xmin = xmin, 
                   xmax = xmax, 
                   ymin = ymin, 
                   ymax = ymax),
                fill = "bisque3", alpha = 0.05) +
   geom_line(aes(x = Date, y = dailyval, color = Site, linetype = Location)) + 
  # geom_point(aes(x = Date2, y = Daily, color = fYear), size = 0.3) +
  scale_color_viridis(option = "turbo", discrete = TRUE) +
   scale_x_date(breaks = "1 month", date_labels = "%b", expand = c(0,0)) + 
  labs(y = "Velocity (ft/s)", color = "Year") + 
  theme_bw() +
   theme(strip.text = element_text(size = 12),
         axis.text = element_text(size = 12),
         axis.title.x = element_blank(),
         axis.title.y = element_text(size = 12),
         legend.position = "top",
         legend.box = "vertical"))
```





# Export Figures
```{r}
# Flow
png(filename = here("analysis_2022", "figures", "plot_flow.png"), width = 5, height = 4, units = "in", pointsize = 12, family = "sans", res = 300)
plot_flow
dev.off()

png(filename = here("analysis_2022", "figures", "plot_flow_2022.png"), width = 5, height = 4, units = "in", pointsize = 12, family = "sans", res = 300)
plot_flow_2022
dev.off()

# Velocity

png(filename = here("analysis_2022", "figures", "plot_velocity.png"), width = 5, height = 4, units = "in", pointsize = 12, family = "sans", res = 300)
plot_vel
dev.off()

png(filename = here("analysis_2022", "figures", "plot_velocity_2022.png"), width = 5, height = 4, units = "in", pointsize = 12, family = "sans", res = 300)
plot_velocity_2022
dev.off()




# 2022 WQ
png(filename = here("analysis_2022", "figures", "plot_cont_2022.png"), width = 9, height = 8, units = "in", pointsize = 12, family = "sans", res = 300)
plot_cont_2022
dev.off()

# png(filename = here("analysis_2022", "figures", "plot_cont_2015_2022.png"), width = 10, height = 7, units = "in", pointsize = 12, family = "sans", res = 300)
# plot_cont_allyears
# dev.off()

# WQ compared years
png(filename = here("analysis_2022", "figures", "plot_cont_2015_2022_averaged_Franks.png"), width = 10, height = 9, units = "in", pointsize = 12, family = "sans", res = 300)
plot_cont_jday_frk
dev.off()

png(filename = here("analysis_2022", "figures", "plot_cont_2015_2022_averaged_Mildred.png"), width = 10, height = 9, units = "in", pointsize = 12, family = "sans", res = 300)
plot_cont_jday_mil
dev.off()

# Comparison Franks and BB
png(filename = here("analysis_2022", "figures", "plot_cont_bb_vs_frk.png"), width = 10, height = 7, units = "in", pointsize = 9, family = "sans", res = 300)
plot_mil_vs_frk
dev.off()
```


