---
title: "plot_toxins"
author: "Catarina Pien"
date: '2022-10-12'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(deltamapr)
library(dplyr)
library(ggplot2)
library(ggspatial)
library(here)
library(readr)
library(lubridate)
library(sf)
library(ggnewscale)
library(viridis())

root <- "analysis_2022/" # this is to tell here where to start
```

Read data
```{r}
# 2022 Data
ct_all <- readRDS(here(root, "data_clean", "ct_all_2022.rds")) %>%
  filter(!Analyte %in% c("Chlorophyll a", "Pheophytin a"),
         !is.na(Stratum2))
# 2021 and 2022 Data
ct_all_years <- readRDS(here(root, "data_clean", "ct_all_years.rds")) %>%
  dplyr::select(-Month) %>%
  mutate(Month = month(Date))

# Spatt data
spatt_data <- read_csv(here(root, "data_clean", "spatt_data.csv")) %>%
  mutate(Month = month(EndDate),
         fMonth = month(EndDate, label = TRUE),
         Duration = EndDate-StartDate)

str(ct_all_years)

unique(ct_all$Analyte)
#ct_all_years2 <- unnest(ct_all_years, geometry)
# sf::st_as_sf(ct_all_years, wkt = "geometry")
# class(ct_all_years$geometry) <- "geometry"
  
ct_stations <- ct_all %>%
  dplyr::select(Study, Station, geometry) %>%
  distinct()
load("./data/Regions.RData")

incidents <-
  readRDS(here("analysis_2022", "data_clean", "incident_data.rds")) %>%
  mutate(fYear = factor(Year),
         Advisory = factor(Advisory, levels = c("No Advisory", "Caution", "Warning", "Danger")))

reg3crop = st_crop(reg3, xmin = -121.9, xmax = -121.2, ymin = 37.65, ymax = 38.4)
```


# Plots

## Map all the toxin stations
```{r}
#This is plot 2-4 in the report
(map_cyano <- ggplot()+
  geom_sf(data = WW_Delta, color = "grey", fill = "lightblue", alpha = 0.3, lwd = 0.5)+
  geom_sf(data =reg3crop, aes(fill = Stratum2), inherit.aes = FALSE, alpha = 0.2)+
  geom_sf(data =ct_stations, aes(color = Study, shape = Study), inherit.aes = FALSE, size = 1.8)+
  viridis::scale_color_viridis(option = "turbo", discrete = TRUE)+
  scale_fill_manual(values = reg3crop$colors, name = NULL, guide = NULL)+
  scale_shape_manual(values = c(7, 2, 15, 3, 8, 18, 1, 6)) +
  theme_bw()+
  scale_x_continuous(limits = c(-122, -121.2)) +
  scale_y_continuous(limits = c(37.65, 38.4))+
  #geom_sf_text(data = Alltoxsf, aes(label = Station), size = 2)
  #geom_sf_text(data = reg3crop, aes(label = Stratum2))+
  annotate("text", x = -121.35, y = 37.7, label = "Vernalis")+
  annotate("text", x = -121.6, y = 37.77, label = "Clifton Court")+
   annotate("text", x = -121.3, y = 37.93, label = "Stockton")+
   annotate("text", x = -121.6, y = 38.02, label = "Franks Tract", size = 3.5)+
  annotation_north_arrow(location = "tr", which_north = "true",
                             pad_x = unit(.1, "in"), pad_y = unit(0.2, "in"),
                             style = north_arrow_fancy_orienteering) +
  annotation_scale(location = "bl", bar_cols = c("black", "white", "black", "white"))  +
  theme(legend.position = c(0.18, 0.25),
        panel.border = element_rect(colour = "black", fill = NA),
        legend.background = element_rect(linetype = 2, size = 0.5, colour = 1),
        axis.title = element_blank()))
```


## Map of recreational advisories and toxin concentrations

### Add recreational advisories for Microcystins, Anatoxins and Cylindrospermopsins
```{r}
#To plot the toxin data, I want to put it in terms of the health
#advisory levels from OEHHA. Here is a dataframe of those levels:
health = data.frame(Analyte = c("Microcystins/Nodularins", "Microcystins/Nodularins", "Microcystins/Nodularins", "Anatoxins","Anatoxins", "Cylindrospermopsins", "Cylindrospermopsins"), Advisory = c(0.8, 6,20, .5, 20, 1, 4),
                    AdviseType = c("Caution\nTier I", "Warning \nTier II","Danger \nTier III", "Caution\nTier I", "Warning \nTier II", "Caution\nTier I", "Warning \nTier II")) %>%
  mutate(AdviseType = factor(AdviseType, levels = c("Caution\nTier I", "Warning \nTier II","Danger \nTier III")))
```

#### Plot: All data facet
This one is in the report
```{r}
ct_all_zeros <- ct_all %>%
  mutate(nonzero = ifelse(Result == 0, "zero", "nonzero"))

(plot_data_regions <- ggplot(ct_all_zeros, aes(x = Date, y = Result, color = nonzero)) + 
    geom_point(aes(shape = Study))+
    scale_color_manual(values = c("black", "gray")) +
    guides(color = "none") + 
    new_scale_colour() +
  geom_hline(data = filter(health, AdviseType != "Danger \nTier III"), aes(yintercept = Advisory, color = AdviseType))+
  scale_color_manual(values = c("yellow", "orange", "red"), name = "Recreational \nAdvisory")+
    scale_shape_manual(values = c(16, 17, 15, 8, 6, 7, 18, 7)) +
  facet_grid(Analyte~Stratum2, scales = "free_y",
             labeller = as_labeller(c(Anabaenopeptins = "Anabaenopeptins", Anatoxins = "Anatoxins", Cylindrospermopsins = "Cylindrospermopsins", Saxitoxin = "Saxitoxins", `Microcystins/Nodularins` = "Microcystins/\nNodularins",
                                      CCF = "CCF", `Lower Sac` = "Lower Sac", `South Delta` = "South Delta", `Upper Sac` = "Upper Sac", `Lower SJ` = "Lower SJ", OMR = "OMR", `Cache/Liberty` = "Cache/Liberty",
                                      `East Delta` = "East Delta",
                                      Franks = "Franks"))) +
  xlab("Month of 2022")+ ylab("Concentration ug/L")+
  scale_x_date(breaks = "2 months", date_labels = "%b")+
  theme_bw()+
  theme(legend.position = "bottom",
        legend.box = "vertical",
        axis.text.x = element_text(angle = 90)))
```

Divided by region (Figure 2-16)
```{r}
(plot_advisories_by_region1 <- ggplot(mic_only, aes(x = Date, y = Result)) + geom_point(aes(shape = Study))+
  geom_hline(data = filter(health, AdviseType != "Danger \nTier III"), aes(yintercept = Advisory, color = AdviseType))+
  scale_color_manual(values = c("yellow", "orange", "red"), name = "Recreational \nAdvisory")+
  facet_grid(Analyte~Stratum2, scales = "free_y") +
  xlab("Month of 2022")+ ylab("Concentration ug/L")+
  scale_x_date(breaks = "2 months", date_labels = "%b", expand = c(0,0))+
  theme_bw()+
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90)))
```

### Health advisories

Combine data to plot only data that is at advisory level
2022 only
```{r}
# If we don't want those with no advisories
mic_only <- ct_all %>%
  filter(!is.na(Advisory)) 

# If we want all detections
toxins_all <- ct_all %>%
  mutate(Advisory = ifelse(is.na(Advisory), "No Advisory", Advisory),
         Advisory = factor(Advisory, levels = c("No Advisory", "Caution", "Warning")))

# 2022 data
advisories <- toxins_all %>%
  filter(Year > 2021,
         Month <12) %>%
  mutate(fMonth = month(Date, label = TRUE))

# 2021 and 2022 data
ct_advis_allyears <- ct_all_years %>%
  filter(Year > 2020) %>%
  mutate(Advisory = ifelse(is.na(Advisory), "No Advisory", Advisory)) %>%
  mutate(Advisory = factor(Advisory, levels = c("No Advisory",  "Caution", "Warning", "Danger")))
```

## Map of 2022 cyanotoxin data only (not incidents)
This is in the report
```{r}
(map_advisories <- ggplot()+
  geom_sf(data = reg3crop, aes(fill = Stratum2), alpha = 0.3) +
  geom_sf(data = WW_Delta, color = "grey", fill = "lightblue")+
  scale_fill_manual(values = reg3$colors, guide = NULL)+
  theme_bw()+ylab("")+xlab("")+
  geom_sf(data = advisories, aes(color = Advisory, shape = Study), size = 3)+
  annotate("text", x = -121.6, y = 37.8, label = "Clifton Court")+
  annotate("text", x = -121.48, y = 37.95, label = "Mildred Island")+
  annotate("text", x = -121.3, y = 37.93, label = "Stockton")+
  annotate("text", x = -121.75, y = 37.99, label = "Big Break")+
  scale_color_manual(values = c("navy", "yellow",  "orange"), labels = c("No Advisory", "Caution", "Warning"), name = "Advisory Level")+
  theme_bw()+ 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          axis.title = element_blank()) + 
  annotation_north_arrow(location = "tr", which_north = "true",
                             pad_x = unit(.1, "in"), pad_y = unit(0.2, "in"),
                             style = north_arrow_fancy_orienteering) +
  annotation_scale(location = "bl", bar_cols = c("black", "white", "black", "white"))  +
  scale_x_continuous(limits = c(-121.9, -121.2)) +
  scale_y_continuous( limits = c(37.7, 38.4)))
```

## 2021 and 2022
(in report)
```{r}
# ct_advis_allyears <- ct_all_years%>%
#   filter(Advisory != "No Advisory",
#          Year > 2020)  %>%
#   mutate(Advisory = factor(Advisory, levels = c("Caution", "Warning", "Danger")))

(map_advisories_allyears <- ggplot()+
  geom_sf(data = reg3crop, aes(fill = Stratum2), alpha = 0.1) +
  geom_sf(data = WW_Delta, color = "grey", fill = "snow2", alpha= 0.5)+
   geom_sf(data = ct_advis_allyears, aes(color = Advisory, shape = Study, size = Advisory))+
   scale_fill_manual(values = reg3$colors, guide = NULL) +
  scale_size_manual(values = c(2, 4, 4, 4)) +
  scale_shape_manual(values = c(16, 17, 15, 8, 6, 7, 18, 7)) +
  theme_bw()+ylab("")+xlab("")+
  facet_wrap(~Year) + 
  annotate("text", x = -121.6, y = 37.8, label = "Clifton Court")+
  annotate("text", x = -121.48, y = 37.95, label = "Mildred Island")+
  annotate("text", x = -121.3, y = 37.93, label = "Stockton")+
  annotate("text", x = -121.75, y = 37.99, label = "Big Break")+
  scale_color_manual(values = c("navy", "#7E03A8FF",  "#E16462FF", "#FCA636FF"), labels = c("No Advisory", "Caution", "Warning", "Danger"), name = "Advisory Level")+
  annotation_north_arrow(location = "tr", which_north = "true",
                             pad_x = unit(.1, "in"), pad_y = unit(0.2, "in"),
                             style = north_arrow_fancy_orienteering) +
  annotation_scale(location = "bl", bar_cols = c("black", "white", "black", "white"))  +
  scale_x_continuous(limits = c(-121.9, -121.2)) +
  scale_y_continuous( limits = c(37.7, 38.4)) +
  theme_bw()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.6),
        strip.text = element_text(size = 12),
        legend.position = "top",
        axis.title = element_blank(),
        legend.box = "vertical") +
  guides(size = "none"))
```

## Plot of 2022 by month
```{r}
(map_advisories_month_2022 <- ggplot()+
  geom_sf(data = WW_Delta, color = "grey", fill = "snow2")+
  geom_sf(data = reg3crop, aes(fill = Stratum2), alpha = 0.1, inherit.aes = FALSE) +
  geom_sf(data = advisories, aes(color = Advisory, size = Advisory, shape = Study), inherit.aes = FALSE) +
  scale_fill_manual(values = reg3$colors, guide = NULL)+
  scale_color_manual(values = c("navy", "#7E03A8FF",  "#E16462FF"), labels = c("No Advisory", "Caution", "Warning"), name = "Advisory Level")+
  #scale_color_manual(values = c("navy", "yellow",  "orange"), labels = c("No Advisory", "Caution", "Warning"), name = "Advisory Level")+
  scale_shape_manual(values = c(16, 17, 15, 8, 6, 7, 18, 7)) +
  scale_size_manual(values = c(2, 4, 4)) +
  facet_wrap(~factor(fMonth)) +
  annotation_north_arrow(location = "tr", which_north = "true",
                          pad_x = unit(0.3, "cm"), pad_y = unit(0.3, "cm"),
                          height = unit(0.75, "cm"),
                         width = unit(0.75, "cm"),
                          style = north_arrow_fancy_orienteering) +
  annotation_scale(location = "bl", bar_cols = c("black", "white", "black", "white"))  +
  scale_x_continuous(limits = c(-121.9, -121.2)) +
  scale_y_continuous(limits = c(37.7, 38.4)) +
  theme_bw()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.6),
        strip.text = element_text(size = 12),
        legend.position = "top",
        axis.title = element_blank(),
        legend.box = "vertical") +
  guides(size = "none"))
```

## Spatt plot
```{r}
(plot_spatt <- ggplot(spatt_data) + geom_col(aes(StartDate, Result, fill = Analyte)) +
  theme_bw())
(tile_spatt <- ggplot(spatt_data) + geom_tile(aes(Month, Site_Name, fill = Result)) + facet_wrap(~Analyte) + theme_bw())


spatt_sum_sf <- filter(spatt_data, Month > 3 & Month <12) %>%
  mutate(ResPerDay = Result/as.numeric(Duration)) %>%
  group_by(Analyte) %>%
  mutate(ResultNorm = (Result - min(Result))/ (max(Result)-min(Result))) %>%
  ungroup() %>%
  st_as_sf(coords =c("Longitude", "Latitude"), remove = FALSE, crs = 4269) 

spatt_monthly_sf <- spatt_sum_sf %>%
  group_by(Month, fMonth, Analyte, Site_Name) %>%
  summarize(maxResult = max(Result, na.rm = TRUE),
            maxNorm = round(max(ResultNorm, na.rm = TRUE),2),
            meanResPerDay = mean(ResPerDay, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(Analyte) %>%
  mutate(Result = case_when(maxResult == 0 ~ "ND",
                              maxResult < 10 ~ "<10",
                               maxResult >= 10 & maxResult < 100 ~ "10-100",
                               maxResult >= 100 & maxResult < 1000 ~ "100-1000",
                               maxResult >= 1000 ~ ">1000"),
         ResultPerDay = case_when(meanResPerDay == 0 ~ "ND",
                              meanResPerDay < 0.1 ~ "<0.1",
                               meanResPerDay >= 0.1 & meanResPerDay < 1 ~ "0.1-1",
                               meanResPerDay >= 1 & meanResPerDay < 10 ~ "1-10",
                               meanResPerDay >= 10 ~ ">10"),
         ResultNorm = ifelse(maxNorm == 0, NA, maxNorm))
       

ggplot(spatt_monthly_sf) + geom_histogram(aes(maxResult), binwidth = 10)
```

Used this plot for spatt results
```{r}

spatt_monthly_sf$Result <- factor(spatt_monthly_sf$Result, levels = c("ND", "<10", "10-100", "100-1000", ">1000"))
spatt_monthly_sf$ResultPerDay <- factor(spatt_monthly_sf$ResultPerDay, levels = c("ND", "<0.1", "0.1-1", "1-10", ">10"))

(map_spatt <- ggplot() + 
    geom_sf(data = WW_Delta, color = "lightcyan3", fill = "lightcyan1", alpha = 0.4) +
  geom_sf(data = spatt_monthly_sf, aes(color = Result), inherit.aes = FALSE) + facet_grid(Analyte~fMonth)+ 
  scale_colour_manual(values = c("gray65", viridis::viridis(5, option = "plasma")[1:4])) +
  scale_x_continuous(limits = c(-121.9, -121.1)) +
  scale_y_continuous(limits = c(37.6, 38.4)) +
  labs(color = "Max SPATT \nConcentration (ng/g)")+
  theme_bw() +
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        strip.text.y = element_text(size = 8),
        legend.position = "top",
        legend.spacing.x = unit(1.0, 'cm')))

(map_spatt_pd <- ggplot() + 
    geom_sf(data = WW_Delta, color = "lightcyan3", fill = "lightcyan1", alpha = 0.9) +
  geom_sf(data = spatt_monthly_sf, aes(color = ResultPerDay), inherit.aes = FALSE) + facet_grid(Analyte~fMonth)+ 
  scale_colour_manual(values = c("gray65", viridis::viridis(5, option = "plasma")[1:4])) +
  scale_x_continuous(limits = c(-121.9, -121.1)) +
  scale_y_continuous(limits = c(37.6, 38.4)) +
  labs(color = "Mean SPATT \nConcentration \nper day (ng/g)")+
  theme_bw() +
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        strip.text.y = element_text(size = 8)))
```

Normalized 
```{r}
(map_spatt_norm <- ggplot() + 
  geom_sf(data = WW_Delta, color = "lightcyan3", fill = "lightcyan1", alpha = 0.2) +
  geom_sf(data = spatt_monthly_sf, aes(color = maxNorm), size = 1.5, inherit.aes = FALSE) + facet_grid(Analyte~fMonth)+ 
  scale_colour_gradientn(colours = c("gray65", viridis::viridis(5, option = "plasma")[1:4])) + 
  scale_x_continuous(limits = c(-121.9, -121.1)) +
  scale_y_continuous(limits = c(37.6, 38.4)) +
  labs(color = "Normalized \nMax SPATT \nConcentration")+
  theme_bw() +
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1),
        strip.text.y = element_text(size = 8), 
        legend.position = "top",
        legend.spacing.x = unit(1.0, 'cm')) +
  guides(color = guide_colourbar(barwidth = 11)))
```



```{r}
ggplot(spatt_summer_sf) + geom_histogram(aes(maxResult)) + facet_wrap(~Analyte, scales= "free") +
  theme_bw()

points <- spatt_monthly_sf %>%
  dplyr::select(Site_Name) %>%
  unique() 
ggplot() + 
   geom_sf(data = WW_Delta, color = "lightcyan3", fill = "lightcyan1", alpha = 0.2) +
  geom_sf_label(data = points, aes(label = Site_Name), inherit.aes = FALSE)

spatt_sum_sf %>%
  group_by(Analyte) %>%
  summarize(min = min(Result),
            max = max(Result))
  
```

# Incident reports (did not use)

Map of 2020, 2021, 2022 incident reports
```{r}
all_data <- incidents %>%
  mutate(fYear = factor(Year),
         Advisory = factor(Advisory, levels = c("Caution", "Warning", "Danger")))%>%
  filter(!(Advisory == "No Advisory"),
         fYear %in% c("2020", "2021", "2022"))

incidents_2022 <- incidents %>%
  filter(!(Advisory == "No Advisory"),
         fYear == "2022") %>%
  mutate(fMonth = lubridate::month(Date, label = TRUE))

levels(all_data$Advisory)
```

```{r}
(map_advisories_all <- ggplot()+
  geom_sf(data = WW_Delta, color = "grey", fill = "lightblue")+
  geom_sf(data = reg3crop, aes(fill = Stratum2), alpha = 0.3) +
  scale_fill_manual(values = reg3$colors, guide = NULL)+
  theme_bw()+ylab("")+xlab("")+
  geom_sf(data = all_data, aes(color = Advisory, shape = Study), size = 3)+
   facet_wrap(~factor(Year)) + 
  scale_color_manual(values = c("yellow", "orange", "red"), labels = c("Caution", "Warning", "Danger"), name = "Incident Reports\nAdvisory Level")+
   annotation_north_arrow(location = "tr", which_north = "true",
                             pad_x = unit(.1, "in"), pad_y = unit(0.2, "in"),
                             style = north_arrow_fancy_orienteering) +
      annotation_scale(location = "bl", bar_cols = c("black", "white", "black", "white"))  +
  scale_x_continuous(limits = c(-121.9, -121.2)) +
  scale_y_continuous( limits = c(37.7, 38.4)) +
  theme_bw()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.6),
        strip.text = element_text(size = 12),
        legend.position = "top"))
```

2022 only
```{r}
(map_advisories_month <- ggplot()+
  geom_sf(data = WW_Delta, color = "grey", fill = "lightblue")+
  geom_sf(data = reg3crop, aes(fill = Stratum2), alpha = 0.3, inherit.aes = FALSE) +
  scale_fill_manual(values = reg3$colors, guide = NULL)+
  
  geom_sf(data = incidents_2022, aes(color = Advisory),  size = 2, inherit.aes = FALSE) +
  scale_color_manual(values = c("yellow", "red"), labels = c("Caution", "Danger"), 
                  name = "Incident Reports\nAdvisory Level") +
  facet_wrap(~factor(fMonth)) +
  annotation_north_arrow(location = "tr", which_north = "true",
                          pad_x = unit(.1, "in"), pad_y = unit(0.2, "in"),
                          style = north_arrow_fancy_orienteering) +
  annotation_scale(location = "bl", bar_cols = c("black", "white", "black", "white"))  +
  scale_x_continuous(limits = c(-121.9, -121.2)) +
  scale_y_continuous(limits = c(37.7, 38.4)) +
  theme_bw()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.6),
        strip.text = element_text(size = 12),
        legend.position = "top",
        axis.title = element_blank()))
```

# Write plots
```{r}
# These are all in the report -----------
png(filename = here("analysis_2022", "figures", "map_cyano.png"), width = 6, height = 6, units = "in", pointsize = 12, family = "sans", res = 300)
map_cyano
dev.off()

png(filename = here("analysis_2022", "figures", "cyano_by_region.png"), width = 8.5, height = 8.5, units = "in", pointsize = 12, family = "sans", res = 300)
plot_data_regions
dev.off()

png(filename = here("analysis_2022", "figures", "map_advisories.png"), width = 6, height = 6, units = "in", pointsize = 12, family = "sans", res = 300)
map_advisories
dev.off()

png(filename = here::here("analysis_2022", "figures", "map_advisories_2021_2022.png"), width = 7, height = 6, units = "in", pointsize = 12, family = "sans", res = 300)
map_advisories_allyears
dev.off()


png(filename = here::here("analysis_2022", "figures", "map_advisories_2022_month.png"), width = 8, height = 8, units = "in", pointsize = 12, family = "sans", res = 300)
map_advisories_month_2022
dev.off()

png(filename = here("analysis_2022", "figures", "spatt_map_2022.png"), width = 7.5, height = 9, units = "in", pointsize = 10, family = "sans", res = 300)
map_spatt
dev.off()

png(filename = here("analysis_2022", "figures", "spatt_map_pd_2022.png"), width = 9, height = 7.5, units = "in", pointsize = 10, family = "sans", res = 300)
map_spatt_pd
dev.off()

png(filename = here("analysis_2022", "figures", "spatt_map_norm_2022.png"), width = 7.5, height = 9, units = "in", pointsize = 10, family = "sans", res = 300)
map_spatt_norm
dev.off()





# Not using these - SWB incidents ----------------------------
png(filename = here("analysis_2022", "figures", "map_advisories_all.png"), width = 8, height = 6, units = "in", pointsize = 12, family = "sans", res = 300)
map_advisories_all
dev.off()

png(filename = here("analysis_2022", "figures", "map_advisories_2022month.png"), width = 8, height = 7, units = "in", pointsize = 12, family = "sans", res = 300)
map_advisories_month
dev.off()
```



# Tables

2-3 Locations of Cyanotoxin Monitoring Data (Study-Station-Lat-Lon-Region)
```{r}

```

2-4 Methods used for Cyanotoxin Analysis by each study
```{r}

```

